---
title: "School Data Cleaner"
author: "Brian Stacy"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 8,
	message = FALSE,
	warning = FALSE
)
library(survey)
library(tidyverse)
library(haven)
library(vtable)
library(here)
library(readxl)
library(stringr)
library(Hmisc)
library(naniar)
library(lubridate)
library(skimr)
library(digest)
library(validate)
library(GGally)
library(srvyr)
library(flextable)
#Country name and year of survey
country_name <-'Pakistan-Balochistan'
country <- "PAK"
year <- '2023'
teach=FALSE


#########################
# File paths #
#########################
#The download_folder will be the location of where raw data is downloaded from the API
#The save_folder will be the location of where cleaned data is stored
dir <- ('C:/Users/wb549384/OneDrive - WBG/Desktop/GEPD-Revamped WF/GEPD_Production-Balochistan')
data_dir <- ('01_GEPD_raw_data/')
processed_dir <- ('03_GEPD_processed_data/')




#########################
# Launch Code
########################


# #launch file to access data from API
school_file<-"epdash.dta"
teacher_file <- "Edo_teacher_level.dta"

#info for weights
weights_file <- "GEPD_Edo_weights_2023-06-20.csv"
strata_info <- c("LGA", "urban_rural")
other_info <- c("Senatorial District", "CLASSIFICATION", "School Type")
school_code_name <-"UBEC SCHOOL CODE"
```

```{r functions}

## Function to save metadata for each question in each module
  makeVlist <- function(dta) { 
    varlabels <- sapply(dta, function(x) attr(x,"label"))
    vallabels <- sapply(dta, function(x) attr(x,"labels"))
    tibble(name = names(varlabels),
           varlabel = varlabels, vallabel = vallabels) 
  }

## Function to save the number of NAs per variable
  makeNAlist <- function(dta) { 
    varlabels <- sapply(dta, function(x) attr(x,"label"))
    vallabels <- sapply(dta, function(x) attr(x,"labels"))
    varmissing <- sapply(dta, function(x) sum(is.na(x)))
    tibble(name = names(varlabels),
           varlabel = varlabels, vallabel = vallabels, varmissing=varmissing) 
  }


bin_var <- function(var, val) {
  case_when(
    var==val  ~ 1,
    var!=val   ~ 0,
    is.na(var) ~ as.numeric(NA))
}



bin_var_2 <- function(var, val) {
  if_else(var==val, 
          as.numeric(1),
          as.numeric(var))
}

bin_var_3 <- function(var, val) {
  case_when(
    var==val  ~ 1,
    TRUE   ~ 0
  )
}


```

```{r indicator}


#Create list of key indicators
ind_list<-c('student_knowledge', 'math_student_knowledge', 'literacy_student_knowledge', 
            'student_proficient', 'student_proficient_70', 'student_proficient_75',
            'literacy_student_proficient', 'literacy_student_proficient_70', 'literacy_student_proficient_75',
            'math_student_proficient', 'math_student_proficient_70', 'math_student_proficient_75',
            'presence_rate','absence_rate', 'sch_absence_rate', 'student_attendance',
            'content_knowledge', 'math_content_knowledge', 'literacy_content_knowledge', 
            'content_proficiency',  'content_proficiency_70', 'content_proficiency_75',
            'literacy_content_proficiency',  'literacy_content_proficiency_70', 'literacy_content_proficiency_75',
            'math_content_proficiency',  'math_content_proficiency_70', 'math_content_proficiency_75',
            'teach_score','classroom_culture','instruction','socio_emotional_skills',
            'teach_prof','classroom_culture_prof','instruction_prof','socio_emotional_skills_prof',
            'ecd_student_proficiency', 'ecd_math_student_proficiency', 'ecd_literacy_student_proficiency', 'ecd_exec_student_proficiency', 'ecd_soc_student_proficiency',
            'ecd_student_knowledge', 'ecd_math_student_knowledge', 'ecd_literacy_student_knowledge', 'ecd_exec_student_knowledge', 'ecd_soc_student_knowledge',
            'inputs', 'blackboard_functional', 'pens_etc', 'textbooks', 'share_desk', 'used_ict', 'access_ict',
            'infrastructure','drinking_water', 'functioning_toilet', 'internet', 'class_electricity','disability_accessibility','disab_road_access', 'disab_school_ramp', 'disab_school_entr', 'disab_class_ramp', 'disab_class_entr', 'disab_screening',
            'operational_management', 'vignette_1', 'vignette_1_resp', 'vignette_1_finance', 'vignette_1_address', 'vignette_2', 'vignette_2_resp', 'vignette_2_finance', 'vignette_2_address', 
            'intrinsic_motivation', 'acceptable_absent', 'students_deserve_attention', 'growth_mindset', 'motivation_teaching',
            'instructional_leadership', 'classroom_observed', 'classroom_observed_recent', 'discussed_observation', 'feedback_observation', 'lesson_plan_w_feedback',
            'principal_knowledge_score', 'add_triple_digit_pknw', 'multiply_double_digit_pknw', 'complete_sentence_pknw', 'experience_pknw', 'textbooks_pknw', 'blackboard_pknw',
            'principal_management', 'sch_goals_exist','sch_goals_clear','sch_goals_relevant','sch_goals_measured',
            'teacher_attraction', 'teacher_satisfied_job', 'teacher_satisfied_status', 'better_teachers_promoted' ,'teacher_bonus', 'salary_delays',
            'teacher_selection_deployment', 'teacher_selection','teacher_deployment',
            'teacher_support', 'pre_service','practicum','in_service','opportunities_teachers_share',
            'teaching_evaluation', 'formally_evaluated', 'evaluation_content', 'negative_consequences','positive_consequences',
            'teacher_monitoring','attendance_evaluated' , 'attendance_rewarded' , 'attendence_sanctions', 'miss_class_admin',
            'sch_management_clarity', 'infrastructure_scfn','materials_scfn','hiring_scfn', 'supervision_scfn', 'student_scfn' , 'principal_hiring_scfn', 'principal_supervision_scfn',
            'standards_monitoring',
            'sch_monitoring', 'monitoring_inputs','monitoring_infrastructure','system_in_place','parents_involved',
            'sch_management_attraction', 'principal_satisfaction',
            'sch_selection_deployment', 
            'sch_support', 'prinicipal_trained','principal_training','principal_used_skills','principal_offered',
            'principal_evaluation', 'principal_formally_evaluated','principal_evaluation_multiple','principal_negative_consequences','principal_positive_consequences'
)

```
## Validation rules
Define set of rules for validating the data
```{r rules}

#teacher effort
EFFT_rules <- validator(
  abs_minmax=in_range(absence_rate,0,100),
  sch_abs_minmax=in_range(sch_absence_rate,0,100),
  abs_nomiss=(!is.na(m2sbq6_efft) | teacher_available==2 | m2saq6!=1 | m2saq4!=3 | is.na(teachcode))
)

#content knowledge
CONT_rules <- validator(
  cont_minmax=in_range(content_knowledge,0,100),
  math_minmax=in_range(math_content_knowledge,0,100),
  lit_minmax=in_range(literacy_content_knowledge,0,100),
  math_lit_cor=cor(math_content_knowledge, literacy_content_knowledge, use="pairwise.complete.obs")>0.2
  )

#student attendance rules
ATTD_rules <- validator(
  attd_minmax=in_range(student_attendance,0,100),
  m4scq4_inpt<=m4scq12_inpt
)

#pedagogy rules
PEDG_rules <- validator(
  class_cult_minmax=in_range(classroom_culture,1,5),
  instruction_minmax=in_range(instruction,1,5),
  socio_emotional_skills_minmax=in_range(socio_emotional_skills,1,5),
  teach_score_minmax=in_range(teach_score,1,5)
  #teach_sum_check=teach_score==(classroom_culture+instruction + socio_emotional_skills)/3
  
)

#4th grade learning
LERN_rules <- validator(
  mat_minmax=in_range(math_student_knowledge,0,100),
  li_minmax=in_range(literacy_student_knowledge,0,100),
  g4_minmax=in_range(student_knowledge,0,100),
  math_lit_cor=cor(math_student_knowledge, literacy_student_knowledge, use="pairwise.complete.obs")>0.2
)

#ECD rules

LCAP_rules <- validator(
  mat_minmax=in_range(ecd_math_student_knowledge,0,100),
  li_minmax=in_range(ecd_literacy_student_knowledge,0,100),
  ex_minmax=in_range(ecd_exec_student_knowledge,0,100),
  so_minmax=in_range(ecd_soc_student_knowledge,0,100),  
  g1_minmax=in_range(ecd_student_knowledge,0,100),
  math_lit_cor=cor(ecd_math_student_knowledge, ecd_literacy_student_knowledge, use="pairwise.complete.obs")>0.2,
  math_ex_cor=cor(ecd_math_student_knowledge, ecd_exec_student_knowledge, use="pairwise.complete.obs")>0.2,
  math_so_cor=cor(ecd_math_student_knowledge, ecd_soc_student_knowledge, use="pairwise.complete.obs")>0.2
)

#inputs
INPT_rules <- validator(
  blackboard_functional=in_range(blackboard_functional,0,1),
  pens_etc=in_range(pens_etc,0,1),
  textbooks=in_range(textbooks,0,1),
  share_desk=in_range(share_desk,0,1),
  used_ict=in_range(used_ict,0,1),
  access_ict=in_range(access_ict,0,1),
  input=in_range(inputs,0,5),
  textbook_pens_cor=cor(pens_etc, textbooks, use="pairwise.complete.obs")>0.2
)

#inputs
INFR_rules <- validator(
  drinking_water=in_range(drinking_water,0,1),
  functioning_toilet=in_range(functioning_toilet,0,1),
  internet=in_range(internet,0,1),
  class_electricity=in_range(class_electricity,0,1),
  disability_accessibility=in_range(disability_accessibility,0,1),
  infra=in_range(infrastructure,0,5),
  textbook_pens_cor=cor(pens_etc, textbooks, use="pairwise.complete.obs")>0.2
)

#operational management
OPMN_rules <- validator(
  vignette_1=in_range(vignette_1,0,2),
  vignette_2=in_range(vignette_2,0,2),
  operational_management=in_range(operational_management,1,5)
)

# Instructional Leadership
ILDR_rules <- validator(
  classroom_observed=in_range(classroom_observed,0,1),
  classroom_observed_recent=in_range(classroom_observed_recent,0,1),
  discussed_observation=in_range(discussed_observation,0,1),
  feedback_observation=in_range(feedback_observation,0,1),
  lesson_plan_w_feedback=in_range(lesson_plan_w_feedback,0,1),
  instructional_leadership=in_range(instructional_leadership,1,5)
)

# Principal knowledge
PKNW_rules <- validator(
  add_triple_digit_pknw=in_range(add_triple_digit_pknw,0,1),
  multiply_double_digit_pknw=in_range(multiply_double_digit_pknw,0,1),
  complete_sentence_pknw=in_range(complete_sentence_pknw,0,1),
  experience_pknw=in_range(experience_pknw,0,1),
  textbooks_pknw=in_range(textbooks_pknw,0,1),
  blackboard_pknw=in_range(blackboard_pknw,0,1),
  principal_knowledge_score=in_range(principal_knowledge_score,1,5)
)

# Principal knowledge
PMAN_rules <- validator(
  sch_goals_exist=in_range(sch_goals_exist,0,1),
  sch_goals_clear=in_range(sch_goals_clear,0,1),
  sch_goals_relevant=in_range(sch_goals_relevant,0,1),
  sch_goals_measured=in_range(sch_goals_measured,0,1),
  problem_solving_proactive=in_range(problem_solving_proactive,0,1),
  problem_solving_info_collect=in_range(problem_solving_info_collect,0,1),
  problem_solving_stomach=in_range(problem_solving_stomach,0,1),
  
  goal_setting=in_range(goal_setting,1,5),
  problem_solving=in_range(problem_solving,1,5),
  principal_management=in_range(principal_management,1,5)
  
)

# Teacher attraction
TATT_rules <- validator(
  teacher_satisfied_job=in_range(teacher_satisfied_job,0,1),
  teacher_satisfied_status=in_range(teacher_satisfied_status,0,1),
  better_teachers_promoted=in_range(better_teachers_promoted,0,1),
  teacher_bonus=in_range(teacher_bonus,0,1),
  salary_delays=in_range(salary_delays,0,12),
  teacher_attraction=in_range(teacher_attraction,1,5)
)

# Teacher Selection and Deployment
TSDP_rules <- validator(
  teacher_selection=in_range(teacher_selection,0,5),
  teacher_deployment=in_range(teacher_deployment,0,5),
  teacher_selection_deployment=in_range(teacher_selection_deployment,1,5)
)

# Teacher Support

TSUP_rules <- validator(
  pre_training_exists=in_range(pre_training_exists,0,.5),
  pre_training_useful=in_range(pre_training_useful,0,.5),
  pre_service=in_range(pre_service,0,1),
  pre_training_practicum=in_range(pre_training_practicum,0,.5),
  pre_training_practicum_lngth=in_range(pre_training_practicum_lngth,0,.5),
  practicum=in_range(practicum,0,1),
  in_service_exists=in_range(in_service_exists,0,1),
  in_service_classroom=in_range(in_service_classroom,0,1),
  pre_training_practicum_lngth=in_range(pre_training_practicum_lngth,0,.5),
  in_service=in_range(in_service,0,1),
  
  teacher_support=in_range(teacher_support,1,5)
)

# Teacher Evaluation

TEVL_rules <- validator(
  formally_evaluated=in_range(formally_evaluated,0,1),
  evaluation_content=in_range(evaluation_content,0,1),
  negative_consequences=in_range(negative_consequences,0,1),
  positive_consequences=in_range(positive_consequences,0,1),
  teaching_evaluation=in_range(teaching_evaluation,1,5)
)

TMNA_rules <- validator(
  attendance_evaluated=in_range(attendance_evaluated,0,1),
  attendance_rewarded=in_range(attendance_rewarded,0,1),
  attendence_sanctions=in_range(attendence_sanctions,0,1),
  miss_class_admin=in_range(miss_class_admin,0,1),
  teacher_monitoring=in_range(teacher_monitoring,1,5)
)

TINM_rules <- validator(
  acceptable_absent=in_range(acceptable_absent,1,5),
  students_deserve_attention=in_range(students_deserve_attention,1,5),
  growth_mindset=in_range(growth_mindset,1,5),
  motivation_teaching=in_range(motivation_teaching,0,1),
  reason_teaching=in_range(bin_var(m3sdq2_tmna,1),0,1),
  intrinsic_motivation=in_range(intrinsic_motivation,1,5)
)

# Input Standards
ISTD_rules <- validator(
  standards_monitoring_input=in_range(standards_monitoring_input,0,1),
  standards_monitoring_infra=in_range(standards_monitoring_infra,0,1),
  standards_monitoring=in_range(standards_monitoring,1,5)
)
# Input Monitoring
IMON_rules <- validator(
  monitoring_inputs=in_range(monitoring_inputs,0,1),
  monitoring_infrastructure=in_range(monitoring_infrastructure,0,1),
  system_in_place=in_range(system_in_place,0,1),
  parents_involved=in_range(parents_involved,0,1),  
  sch_monitoring=in_range(sch_monitoring,1,5)
)

#clarity of functions
SCFN_rules <- validator(
  infrastructure_scfn=in_range(infrastructure_scfn,0,1),
  materials_scfn=in_range(materials_scfn,0,1),
  hiring_scfn=in_range(hiring_scfn,0,1),
  supervision_scfn=in_range(supervision_scfn,0,1),  
  student_scfn=in_range(student_scfn,0,1),  
  principal_hiring_scfn=in_range(principal_hiring_scfn,0,1),  
  supervision_scfn=in_range(supervision_scfn,0,1),  
  sch_management_clarity=in_range(sch_management_clarity,1,5)
)

SATT_rules <- validator(
  principal_satisfaction=in_range(principal_satisfaction,1,5),
  principal_salary=principal_salary>0,
  principal_salary_score=in_range(principal_salary_score,1,5),
  sch_management_attraction=in_range(sch_management_attraction,1,5)
)

SSLD_rules <- validator(
  sch_selection_deployment=in_range(sch_selection_deployment,1,5)
)

SSUP_rules <- validator(
  prinicipal_trained=in_range(prinicipal_trained,0,1),
  principal_training=in_range(principal_training,0,1),
  principal_used_skills=in_range(principal_used_skills,0,1),
  principal_offered=in_range(principal_offered,0,1),
  sch_support=in_range(sch_support,1,5)
)

SEVL_rules <- validator(
  principal_formally_evaluated=in_range(principal_formally_evaluated,0,1),
  principal_evaluation_multiple=in_range(principal_evaluation_multiple,0,1),
  principal_negative_consequences=in_range(principal_negative_consequences,0,1),
  principal_positive_consequences=in_range(principal_positive_consequences,0,1),
  principal_evaluation=in_range(principal_evaluation,1,5)
)
```


# Load Data


```{r data}

#read in sampling frame
#Load original sample of schools

sample_folder <- file.path(paste0(data_dir, "/Sampling/", sep="/"))

data_set_updated <- read_csv(paste(sample_folder, weights_file , sep="")) %>%
  select(school_code_name, strata_info, other_info, strata_prob, ipw
         ) %>%
  unite(strata,strata_info, sep=" - ", remove=FALSE) %>%
  #check if column has a space in the title, and if so do a name repair
  rename_at(
    c(strata_info, other_info),
    ~ str_replace(., " ", "_")
  ) %>%
  rename(school_code=!! school_code_name) %>%
  #create a new column called "strata" that is a combination of the strata and other_info columns
  #drop a duplicate
  filter(!(school_code==12140130 & LGA=="Uhunmwode"))

# check in strata and other_info if there are any values with spaces and if so remove and add a _
strata_info <- str_replace_all(strata_info, " ", "_")
other_info <- str_replace_all(other_info, " ", "_")

###########################
#read in school level file
###########################
school_dta<-read_dta(here(data_dir,"School", school_file))

#rename a few key variables up front
school_dta<- school_dta %>%
  filter(!is.na(school_info_correct)) %>%
  mutate(enumerator_name_other= m1s0q1_name_other  ,
         enumerator_number=m1s0q1_name ,
         survey_time=m1s0q8,
         lat=m1s0q9__Latitude,
         lon=m1s0q9__Longitude,
         school_code=as.numeric(school_code_preload),
         m7_teach_count_pknw=m7_teach_count, #this variable was mistakenly not tagged as pknw
         total_enrolled=m1saq7) %>%
  select(-starts_with("enumerators_preload")) %>% 
  filter(!is.na(school_code)) 

#join to data_set_updated file of schools in the frame
school_dta <- school_dta %>%
  left_join(data_set_updated, by=c("school_code"="school_code")) %>% 
  filter(!is.na(school_code)) 

#check for duplicates in school code
t <- school_dta %>% 
  group_by(school_code) %>%
  summarise(n=n()) %>%
  filter(n>1) %>%
  select(school_code) %>%
  distinct()

#add weight info
school_dta <- school_dta %>%
  group_by(school_code) %>%
  mutate(
    school_weight=1/strata_prob,
    g4_stud_count = mean(m4scq4_inpt, na.rm=TRUE)
  ) %>% ungroup() %>%
  filter(!is.na(school_weight))

preamble_info <- c( 'interview__key', 'school_code',
                   'school_name_preload', 
                   'school_province_preload', 'school_district_preload', 'school_emis_preload', 'school_emis_preload',
                   'school_info_correct', 'm1s0q2_name', 'm1s0q2_code', 'm1s0q2_emis',
                   'survey_time', 'lat', 'lon' , 'total_enrolled' , 'm7saq10', 'm1saq4',
                   'school_code', 'strata', strata_info, other_info, 'school_weight', 
                   'numEligible', 'numEligible4th',
                   'm6_class_count', 
                    'm4scq4_inpt', 'g4_stud_count'
                   )


school_merge_temp <- school_dta %>%
  select( preamble_info) %>%
  group_by(school_code) %>%
  mutate(
    numEligible=mean(numEligible, na.rm=TRUE), 
    numEligible4th=mean(numEligible4th, na.rm=TRUE)
  )

school_collapse_temp <- school_dta %>%
  group_by(school_code) %>%
  select( preamble_info) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) 


############################
#read in teacher roster file
############################

##########
# Addtional Cleaning may be required here to link the various modules
# We are assuming the teacher level modules (Teacher roster, Questionnaire, Pedagogy, and Content Knowledge have already been linked here)
# See Merge_Teacher_Modules code folder for help in this task if needed
##########

teachers_dta<-read_dta(here(data_dir,"School", teacher_file )) %>%
  mutate(teacher_name=m2saq2,
         teacher_number=TEACHERS__id) %>%
  left_join(school_merge_temp %>% select(interview__key, school_code, strata, strata_info, other_info, school_weight, numEligible, numEligible4th )) %>%
  filter(!is.na(TEACHERS__id)) %>%
  mutate( #revert a change that was made to recode
    m2saq3=case_when(
      m2saq3==1 ~ 2,
      m2saq3==0 ~ 1
    )
  )


#rename a few key variables up front
teachers_dta<- teachers_dta %>%
  mutate(teacher_name=m3sb_troster  ,
         teacher_number=m3sb_tnumber ,
         available=m3s0q1,
         teacher_position=m3saq1,
         teacher_grd1=bin_var(m3saq2__1,1),
         teacher_grd2=bin_var(m3saq2__2,1),
         teacher_grd3=bin_var(m3saq2__3,1),
         teacher_grd4=bin_var(m3saq2__4,1),
         #teacher_grd5=bin_var(m3saq2_5,1),
         teacher_language=bin_var(m3saq3__1,1),
         teacher_math=bin_var(m3saq3__2,1),
         teacher_both_subj=bin_var(m3saq3__3,1),
         teacher_other_subj=bin_var(m3saq3__97,1),
         teacher_education=m3saq4,
         teacher_year_began=m3saq5,
         teacher_age=m3saq6,
  )

teachers_dta<- teachers_dta %>%
  mutate(temp=rowSums(select(.,teacher_grd1, teacher_grd2, teacher_grd3, teacher_grd4))) %>% # here we count the number of grades present in the classroom
  mutate(multigrade=case_when(temp > 1 ~ 1,
                              TRUE ~ 0)) %>% #this variable is equal to 1 if there are several grades and zero otherwise
  select(-temp)


#  We create a unique grade variable
teachers_dta <- teachers_dta %>%
  mutate(grade=case_when(teacher_grd1==1 & multigrade!=1 ~ 1,
                         teacher_grd2==1 & multigrade!=1 ~ 2,
                         teacher_grd3==1 & multigrade!=1 ~ 3,
                         teacher_grd4==1 & multigrade!=1 ~ 4,
                         #teacher_grd5==1 & multigrade!=1 ~ 5,
                         multigrade==1 ~ 6,
                         TRUE ~ NA_real_)) %>%
  mutate(grade=factor(grade, levels=c(1,2,3,4,6), labels=c("Grade 1", "Grade 2", "Grade 3", "Grade 4", "Multigrade")))


#get some usual info for weighting
teachers_dta <- teachers_dta %>%
  group_by(school_code) %>%
  mutate(
    g4_teacher_count=sum(m3saq2__4, na.rm=TRUE),
    g1_teacher_count=sum(m3saq2__1, na.rm=TRUE)
  )

#teacher weights
teachers_dta <- teachers_dta %>%
  group_by(school_code) %>%
  mutate(
    #absence
    #count number of teachers with non-missing data for m2sbq6_efft
    teacher_abs_count=sum(!is.na(m2sbq6_efft)),
    teacher_abs_weight=numEligible/teacher_abs_count,
    teacher_abs_weight=if_else(is.na(teacher_abs_weight),1,teacher_abs_weight), # fix issues where no g1 teachers listed. Can happen in very small schools
    teacher_abs_comb_weight=school_weight*teacher_abs_weight,
    
    #questionnaire
    teacher_quest_count=sum(!is.na(m3s0q1)),
    teacher_questionnaire_weight=numEligible4th/teacher_quest_count,
    teacher_questionnaire_weight=if_else(is.na(teacher_questionnaire_weight),1,teacher_questionnaire_weight), # fix issues where no g1 teachers listed. Can happen in very small schools
    teacher_quest_comb_weight=school_weight*teacher_questionnaire_weight,
    
    # content knowledge
    teacher_content_count=sum(!is.na(m3s0q1)),
    teacher_content_weight=numEligible4th/teacher_content_count,
    teacher_content_weight=if_else(is.na(teacher_content_weight),1,teacher_content_weight), # fix issues where no g1 teachers listed. Can happen in very small schools
    teacher_content_comb_weight=school_weight*teacher_content_weight,
    
    #pedagogy
    teacher_pedagogy_weight=numEligible4th/1,
    teacher_pedagogy_weight=if_else(is.na(teacher_pedagogy_weight),1,teacher_pedagogy_weight), # fix issues where no g1 teachers listed. Can happen in very small schools
    teacher_pedagogy_comb_weight=school_weight*teacher_pedagogy_weight
  ) %>% ungroup() %>%
  filter(!is.na(school_weight))

#save to processed_dir
write_dta(teachers_dta, here(processed_dir,"School","Confidential","Merged", "teachers_R.dta"))

# add some needed infor for weighting
teachers_school <- teachers_dta %>%
  group_by(school_code) %>%
  select(g1_teacher_count, g4_teacher_count) %>%
  summarise(g1_teacher_count=mean(g1_teacher_count, na.rm=TRUE),
            g4_teacher_count=mean(g4_teacher_count, na.rm=TRUE)) 

school_merge_temp <- school_merge_temp %>%
  left_join(teachers_school)

########
# 1st Grade
########

first_grade <- read_dta(here(data_dir, "School", "ecd_assessment.dta")) %>%
  left_join(school_merge_temp)

#add weights
first_grade <- first_grade %>%
  mutate(
    g1_class_weight=g1_teacher_count/1, #weight is the number of 1st grade streams divided by number selected (1)
    g1_class_weight=if_else(g1_class_weight<1,1,g1_class_weight)
  ) %>%
  group_by(school_code) %>%
  mutate(
    g1_assess_count=sum(!is.na(ecd_assessment__id))
  ) %>%
  ungroup() %>%
  mutate(
    g1_student_weight_temp=m6_class_count/g1_assess_count,
    g1_stud_weight=g1_class_weight*g1_student_weight_temp,
    g1_comb_weight=school_weight*g1_stud_weight) %>%
  filter(!is.na(school_weight))

#save
write_dta(first_grade, here(processed_dir,"School","Confidential","Merged", "first_grade_assessment_R.dta"))

######
# Grade 4 data
######
fourth_grade <- read_dta(here(data_dir, "School", "fourth_grade_assessment.dta")) %>%
  left_join(school_merge_temp)

## add weights

fourth_grade <- fourth_grade %>%
  mutate(
    g4_class_weight=g4_teacher_count/1, #weight is the number of 4th grade streams divided by number selected (1)
    g4_class_weight=if_else(g4_class_weight<1,1,g4_class_weight)
  ) %>%
  group_by(school_code) %>%
  mutate(
    g4_assess_count=sum(!is.na(fourth_grade_assessment__id))
  ) %>%
  ungroup() %>%
  mutate(
    g4_student_weight_temp=g4_stud_count/g4_assess_count,
    g4_stud_weight=g4_class_weight*g4_student_weight_temp,
    g4_comb_weight=school_weight*g4_stud_weight) %>%
  filter(!is.na(school_weight))

#save
write_dta(fourth_grade, here(processed_dir,"School","Confidential","Merged", "fourth_grade_assessment_R.dta"))

# return to school and save

#collapse to single observation by school_code
school_dta <- school_dta %>%
  group_by(school_code) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.))) %>%
  ungroup() %>%
  filter(!is.na(ipw))

# save
write_dta(school_dta, here(processed_dir,"School","Confidential","Merged", "school_R.dta"))

```



# Teachers

## Teacher Absence

```{r efft}

#############################################
##### Teacher Absence ###########
#############################################

# School survey. Percent of teachers absent. Teacher is coded absent if they are: 
#   - not in school 
# - in school but absent from the class 
# - in the class but not teaching.






#create indicator for whether each teacher was absent from school
teachers_dta <- teachers_dta %>%
  mutate(sch_absence_rate=100*case_when(
    (m2sbq6_efft==6 | teacher_available==2) & !is.na(m2sbq6_efft) ~ 1,
    m2sbq6_efft!=6 & !is.na(m2sbq6_efft)   ~ 0,
    is.na(m2sbq6_efft) ~ as.numeric(NA)))

#create indicator for whether each teacher was absent from classroom or school
teachers_dta <- teachers_dta %>%
  mutate(absence_rate=100*case_when(
    (m2sbq6_efft==6 | m2sbq6_efft==5 |  teacher_available==2) & !is.na(m2sbq6_efft) ~ 1,
    (m2sbq6_efft==1 | m2sbq6_efft==3 | m2sbq6_efft==2 | m2sbq6_efft==4)  & !is.na(m2sbq6_efft) ~ 0,
    is.na(m2sbq6_efft) ~ as.numeric(NA)) )

#create indicator for whether each principal was absent from school
teachers_dta <- teachers_dta %>%
  mutate(principal_absence=100*case_when(
    m2sbq3_efft==8 & !is.na(m2sbq3_efft) ~ 1,
    m2sbq3_efft!=8 & !is.na(m2sbq3_efft)   ~ 0,
    is.na(m2sbq3_efft) ~ as.numeric(NA))) %>%
  mutate(absence_rate=if_else(is.na(absence_rate), principal_absence, absence_rate ),
         sch_absence_rate=if_else(is.na(sch_absence_rate), principal_absence, sch_absence_rate ),
         presence_rate=100-absence_rate)


#set up survey and calculate summary stats
teachers_dta %>%
  ungroup() %>%
  as_survey_design(
                   ids=c(school_code,TEACHERS__id),
                   strata=strata,
                   weights=c(school_weight, teacher_abs_weight)
                   ) %>%
  summarise(
    #get mean for each variable (absence_rate, sch_absence_rate, presence_rate)
    absence_rate_mean=survey_mean(absence_rate, na.rm=TRUE),
    sch_absence_rate_mean=survey_mean(sch_absence_rate, na.rm=TRUE),
    presence_rate_mean=survey_mean(presence_rate, na.rm=TRUE)
  ) %>%
  #pivot longer
  pivot_longer(cols=contains("mean"), names_to="variable", values_to="value") %>%
  flextable() %>%
  add_header_lines("Teacher Absence Estimates")




#validate 
out <- confront(teachers_dta, EFFT_rules)
summary(out)
plot(out)
```

## Teacher Pedagogy

```{r include=teach}

  #############################################
  ##### Teacher Pedagogical Skill ###########
  #############################################

  #define variables for TEACH
  # label variables

  

  

#validate 
out <- confront(teachers_dta, PEDG_rules)
summary(out)
plot(out)
```


## Teacher Content Knowledge

```{r}

#############################################
##### Teacher Knowledge ###########
#############################################



#recode assessment variables to be 1 if student got it correct and zero otherwise
teachers_dta<- teachers_dta %>%
  mutate_at(vars(starts_with("m5s1q"), starts_with("m5s2q")), ~bin_var_2(.,2)  ) %>%
  mutate_at(vars(starts_with("m5s1q"), starts_with("m5s2q")), ~bin_var(.,1)  )



####Literacy####
#calculate # of literacy items
#note: grep is a tool for searching text with specified pattern.  In our case, we are looking for m5s1q, which is the prefix of literacy items

#calculate teachers lit items correct
teachers_dta <- teachers_dta %>%
  mutate(literacy_content_knowledge=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s1q")], na.rm=TRUE),
         correct_letter=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s1q3")], na.rm=TRUE),
         cloze=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s1q2")], na.rm=TRUE),
         grammar=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s1q1")], na.rm=TRUE),
         read_passage=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s1q4")], na.rm=TRUE))

####Math####
#calculate # of math items

#calculate teachers math items correct
teachers_dta <- teachers_dta %>%
  mutate(math_content_knowledge=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="m5s2q")], na.rm=TRUE),
         arithmetic_number_relations=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="number")], na.rm=TRUE),
         geometry=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="geometric")], na.rm=TRUE),
         interpret_data=100*rowMeans(.[grep(x=colnames(teachers_dta), pattern="data")], na.rm=TRUE))



teachers_dta <- teachers_dta %>%
  group_by(school_code) %>%
  mutate(
    content_knowledge=case_when(
      !is.na(literacy_content_knowledge) & !is.na(math_content_knowledge) ~ (literacy_content_knowledge+math_content_knowledge)/2,
      !is.na(literacy_content_knowledge) & is.na(math_content_knowledge) ~ literacy_content_knowledge,
      is.na(literacy_content_knowledge) & !is.na(math_content_knowledge) ~ math_content_knowledge,
      TRUE ~ as.numeric(NA)
    ),
    content_proficiency=if_else(content_knowledge>=80, 100, 0),
    math_content_proficiency=if_else(math_content_knowledge>=80, 100, 0),
    literacy_content_proficiency=if_else(literacy_content_knowledge>=80, 100, 0),
    m5_teach_count=sum(!is.na(content_knowledge)))




#validate 
out <- confront(teachers_dta, CONT_rules)
summary(out)
plot(out)

```

# Leaners


## Student Attendance

```{r}

#############################################
##### Student Attendance ###########
#############################################

#Percent of 4th grade students who are present during an unannounced visit.

school_dta<- school_dta %>%
  mutate(student_attendance=m4scq4_inpt/m4scq12_inpt) %>%
  mutate(student_attendance=if_else(m4scq4_inpt>m4scq12_inpt, m4scq12_inpt/m4scq4_inpt,as.numeric(student_attendance)))  %>% #fix an issue where sometimes enumerators will get these two questions mixed up.
  mutate(student_attendance=if_else(student_attendance>1, 1, as.numeric(student_attendance)))  %>% #fix an issue where sometimes enumerators will get these two questions mixed up.
  mutate(student_attendance=100*student_attendance) 


ggplot(school_dta, aes(x=student_attendance)) +
  geom_density() +
  ggtitle('Student Attendance')

#validate 
out <- confront(school_dta, ATTD_rules)
summary(out)
plot(out)

```

## 4th Grade Student Achievement

```{r}

  
  #############################################
#############################################
##### 4th Grade Assessment ###########
#############################################

#create indicator for % correct on student assessment
#Note:  in the future we could incorporate irt program like mirt


#rename a few key variables up front
fourth_grade<- fourth_grade %>%
  mutate(student_name=m8s1q1  ,
         student_number=fourth_grade_assessment__id,
         student_age=m8s1q2,
         student_male=bin_var(m8s1q3,1),
  )


# create a function to score questions m8saq2 and m8saq3, in which students identify letters/words that enumerator calls out.
# This question is tricky, because enumerators would not always follow instructions to say out loud the same letters/words
# In order to account for this, will assume if 80% of the class has a the exact same response, then this is the letter/word called out
# Score this so that if there is a deviation from what 80% of the class says, then it is wrong.
call_out_scorer <- function(var, pctl) {
  1-abs(var - quantile(var, pctl, na.rm=T))
}



#recode assessment variables to be 1 if student got it correct and zero otherwise
fourth_grade<- fourth_grade %>%
  mutate_at(vars(starts_with("m8saq5"), 
                 starts_with("m8saq6"),
                 starts_with("m8sbq2"),
                 starts_with("m8sbq3"),
                 starts_with("m8sbq4"),
                 starts_with("m8sbq5"),
                 starts_with("m8sbq6"),
  ), ~bin_var(.,1)  ) %>% #now handle the special cases
  mutate(m8saq4_id=if_else(m8saq4_id==5,4, as.numeric(m8saq4_id))) %>% #fix case where some enumerators recorded the pre-filled answer.
  mutate(m8saq7a_gir=bin_var(m8saq7a_gir, 3),
         m8saq7b_gir=bin_var(m8saq7b_gir, 3),
         m8saq7c_gir=bin_var(m8saq7c_gir, 2),
         m8saq7d_gir=bin_var(m8saq7d_gir, 3),
         m8saq7e_gir=bin_var(m8saq7e_gir, 4),
         m8saq7f_gir=bin_var(m8saq7f_gir, 1),
         m8saq7g_gir=bin_var(m8saq7g_gir, 2),
         m8saq7h_gir=bin_var(m8saq7h_gir, 2),
         m8saq7i_gir=bin_var(m8saq7i_gir, 4),
         m8saq7j_gir=bin_var(m8saq7j_gir, 1),
         m8saq7k_gir=bin_var(m8saq7k_gir, 3)) %>% #grade lonely giraffe question
  group_by(school_code) %>%
  mutate_at(vars(starts_with("m8saq2_id"),starts_with("m8saq3_id"), starts_with("m8sbq1_number_sense")),
            ~call_out_scorer(.,0.8)) %>%
  ungroup() %>%
  mutate(m8saq2_id=(rowSums(.[grep(x=colnames(fourth_grade), pattern="m8saq2_id")])-7)/3, #subtract some letters not assessed and make out of 3 points
         m8saq3_id=(rowSums(.[grep(x=colnames(fourth_grade), pattern="m8saq3_id")])-7)/3) %>%
  mutate(m8saq2_id=if_else(m8saq2_id<0,0,m8saq2_id), #subtract some letters not assessed and make out of 3 points
         m8saq3_id=if_else(m8saq3_id<0,0,m8saq3_id)) %>%
  mutate(m8saq2_id=if_else(m8saq2_id>1,1,m8saq2_id), #subtract some letters not assessed and make out of 3 points
         m8saq3_id=if_else(m8saq3_id>1,1,m8saq3_id)) %>%
  mutate(m8saq4_id=if_else(m8saq4_id!=99, m8saq4_id/4,0),
         m8saq7_word_choice=bin_var(m8saq7_word_choice,2),
         m8sbq1_number_sense=(rowSums(.[grep(x=colnames(fourth_grade), pattern="m8sbq1_number_sense")])-7)/3)         %>%
    mutate( 
      m8sbq1_number_sense=if_else(m8sbq1_number_sense<0,0,m8sbq1_number_sense)) %>%
    mutate(
      m8sbq1_number_sense=if_else(m8sbq1_number_sense>1,1,m8sbq1_number_sense)) %>%
  select(-starts_with("m8saq2_id_"),-starts_with("m8saq3_id_"),-starts_with("m8sbq1_number_sense_"))


####Literacy####
#calculate # of literacy items
#note: grep is a tool for searching text with specified pattern.  In our case, we are looking for m8s1q, which is the prefix of literacy items

#calculate students lit items correct
fourth_grade <- fourth_grade %>%
  mutate(literacy_student_knowledge=100*rowMeans(.[grep(x=colnames(fourth_grade), pattern="m8saq")], na.rm=TRUE))
         #literacy_student_knowledge_nogiraffe=100*rowMeans(.[c('m8saq4_id', 'm8saq5_story', 'm8saq6_story', 'm8saq7_word_choice', 'm8saq2_id', 'm8saq3_id')], na.rm=TRUE))

####Math####
#calculate # of math items


#calculate students math items correct
fourth_grade <- fourth_grade %>%
  mutate(math_student_knowledge=100*rowMeans(.[grep(x=colnames(fourth_grade), pattern="m8sbq")], na.rm=TRUE))

####Total score####
#calculate students percent correct
fourth_grade <- fourth_grade %>%
  mutate(student_knowledge=(math_student_knowledge+literacy_student_knowledge)/2) %>%
  mutate(student_proficient=100*as.numeric(student_knowledge>=82.9), #34/41
         #student_proficient_nogiraffe=100*as.numeric((literacy_student_knowledge_nogiraffe+math_student_knowledge)/2>=86.6), #12/13 points
         student_proficient_70=100*as.numeric(student_knowledge>=70),
         student_proficient_75=100*as.numeric(student_knowledge>=75),
         #literacy_student_proficient_nogiraffe=100*as.numeric(literacy_student_knowledge_nogiraffe>=92), #12/13 points
         literacy_student_proficient=100*as.numeric(literacy_student_knowledge>=83.3), #20/24 points
         literacy_student_proficient_70=100*as.numeric(literacy_student_knowledge>=70),
         literacy_student_proficient_75=100*as.numeric(literacy_student_knowledge>=75),
         math_student_proficient=100*as.numeric(math_student_knowledge>=82), #14/17 points
         math_student_proficient_70=100*as.numeric(math_student_knowledge>=70),
         math_student_proficient_75=100*as.numeric(math_student_knowledge>=75))






#plots
ggplot(fourth_grade, aes(x=student_knowledge)) +
  geom_density() +
  ggtitle('4th Grade Student Score Distribution')


ggpairs(fourth_grade, columns=c("student_knowledge", "math_student_knowledge", "literacy_student_knowledge" ), title="4th Grade Student Scores") +
  theme_bw()


#validate 
out <- confront(fourth_grade, LERN_rules)
summary(out)
plot(out)
```

## ECD

```{r}

#############################################
##### ECD Assessment ###########
#############################################

# School survey. Fraction correct on the Early Childhoold Assessment given to students in school.






first_grade<- first_grade %>%
  mutate(ecd_student_name=m6s1q1  ,
         ecd_student_number=ecd_assessment__id,
         ecd_student_age=m6s1q2,
         ecd_student_male=bin_var(m6s1q3,1),
         ecd_consent=bin_var(m6s1q4,1)
  ) %>% 
  rename( #rename this variable to avoid dropping when I run anonymization program later
    m6s2q6a_nm_writing=m6s2q6a_name_writing,
    m6s2q6b_nm_writing_response=m6s2q6b_name_writing
  )

list_topics<-c("vocabn", "comprehension","letters","words","sentence","nm_writing","print",
               "countingproduce_set","number_ident","number_compare","simple_add",
               "backward_digit","head_shoulders",
               "perspective","conflict_resol")



#recode ECD variables to be 1 if student got it correct and zero otherwise
first_grade<- first_grade %>%
  mutate_at(vars(ends_with("comprehension"),
                 ends_with("letters"),
                 ends_with("words"),
                 ends_with("sentence"),
                 ends_with("nm_writing"),
                 ends_with("print"),
                 ends_with("produce_set"),
                 ends_with( "number_ident"),
                 ends_with("number_compare"),
                 ends_with("simple_add"),
                 ends_with("backward_digit"),
                 ends_with("perspective"),
                 ends_with("conflict_resol")), ~bin_var(.,1)  ) %>%
  mutate_at(vars(ends_with("head_shoulders")), ~if_else(.x==2,1,0,missing=NULL)) %>%
  mutate_at(vars(ends_with("vocabn")), ~case_when(.x==98 ~ as.numeric(NA),
                                                  .x==99 ~ 0,
                                                  .x==77 ~ 0,
                                                  (.x!=98 & .x!=99 & .x>=10) ~ 1,
                                                  (.x!=98 & .x!=99 & .x<10) ~ as.numeric(.x)/10,
                                                  is.na(.x) ~ as.numeric(NA))) %>%
  mutate_at(vars(ends_with("counting")), ~case_when(.x==98 ~ as.numeric(NA),
                                                    .x==99 ~ 0,
                                                    .x==77 ~ 0,
                                                    (.x!=98 & .x!=99 & .x>=30) ~ 1,
                                                    (.x!=98 & .x!=99 & .x<30) ~ as.numeric(.x)/30,
                                                    is.na(.x) ~ as.numeric(NA)))



####Literacy####
#calculate # of literacy items
#note: grep is a tool for searching text with specified pattern.  In our case, we are looking for m8s1q, which is the prefix of literacy items


lit_items<-colnames(first_grade[,str_detect(
  colnames(first_grade), "vocabn|comprehension|letters|words|sentence|nm_writing$|print")])

first_grade$literacy_length<-length(lit_items)

#calculate students lit items correct
first_grade <- first_grade %>%
  mutate(ecd_literacy_student_knowledge=100*rowSums(.[grep(x=colnames(first_grade), 
                                                   pattern="vocabn|comprehension|letters|words|sentence|nm_writing$|print")], na.rm=TRUE)/literacy_length)

####Math####
#calculate # of math items

math_items<-colnames(first_grade[,str_detect(
  colnames(first_grade), "counting|produce_set|number_ident|number_compare|simple_add")])

first_grade$math_length<-length(math_items)


#calculate students math items correct
first_grade <- first_grade %>%
  mutate(ecd_math_student_knowledge=100*rowSums(.[grep(x=colnames(first_grade), 
                                               pattern="counting|produce_set|number_ident|number_compare|simple_add")], na.rm=TRUE)/math_length)

####Executive Functioning####
#calculate # of Exec Function items

exec_items<-colnames(first_grade[,str_detect(
  colnames(first_grade), "backward_digit|head_shoulders")])

first_grade$exec_length<-length(exec_items)


#calculate students excec items correct
first_grade <- first_grade %>%
  mutate(ecd_exec_student_knowledge=100*rowSums(.[grep(x=colnames(first_grade), 
                                               pattern="backward_digit|head_shoulders")], na.rm=TRUE)/exec_length)

####Socio-Emotional####
#calculate # of Exec Function items

#NOTE:  Ending persepectives and conflict resolution in $ is a grep trick to make sure columns with trailing characters aren't included.  
#This means specifically the perspetive_responses conflict_resol_responses columns, which are text and just for quality control.
soc_items<-colnames(first_grade[,str_detect(
  colnames(first_grade), "perspective$|conflict_resol$")])

first_grade$soc_length<-length(soc_items)


#calculate students excec items correct
first_grade <- first_grade %>%
  mutate(ecd_soc_student_knowledge=100*rowSums(.[grep(x=colnames(first_grade), 
                                              pattern="perspective$|conflict_resol$")], na.rm=TRUE)/soc_length)

####Total score####
#calculate students percent correct
first_grade <- first_grade %>%
  mutate(ecd_student_knowledge=(ecd_math_student_knowledge+ecd_literacy_student_knowledge+
                                  ecd_exec_student_knowledge + ecd_soc_student_knowledge)/4) %>%
  mutate(ecd_student_proficiency=100*as.numeric(ecd_student_knowledge>=80),
         ecd_math_student_proficiency=100*as.numeric(ecd_math_student_knowledge>=80),
         ecd_literacy_student_proficiency=100*as.numeric(ecd_literacy_student_knowledge>=80),
         ecd_exec_student_proficiency=100*as.numeric(ecd_exec_student_knowledge>=80),
         ecd_soc_student_proficiency=100*as.numeric(ecd_soc_student_knowledge>=80)
  ) 



ggpairs(first_grade, columns=c("ecd_student_knowledge", "ecd_math_student_knowledge", "ecd_literacy_student_knowledge",    "ecd_exec_student_knowledge", "ecd_soc_student_knowledge" ), title="1st Grade Student Scores") +
  theme_bw()


#validate 
out <- confront(first_grade, LCAP_rules)
summary(out)
plot(out)

```

# Input and Infrastructure

## School Inputs

```{r}

#functioning blackboard and chalk
school_dta <- school_dta %>%
  mutate(blackboard_functional=case_when(
    m4scq10_inpt==1 & m4scq9_inpt==1 & m4scq8_inpt==1  ~ 1,
    m4scq10_inpt==0 | m4scq9_inpt==0 | m4scq8_inpt==0 ~ 0)) 

#pens, pencils, textbooks, exercise books
school_dta <- school_dta %>%
  mutate(share_textbook=(m4scq5_inpt)/(m4scq4_inpt)) %>%
  mutate(share_pencil=(m4scq6_inpt)/(m4scq4_inpt)) %>%
  mutate(share_exbook=(m4scq7_inpt)/(m4scq4_inpt)) %>%
  mutate(pens_etc=case_when(
    share_pencil>=0.9 & share_exbook>=0.9  ~ 1,
    share_pencil<0.9 | share_exbook<0.9 ~ 0),
    textbooks=case_when(
      share_textbook>=0.9   ~ 1,
      share_textbook<0.9  ~ 0)) 

#basic classroom furniture
school_dta <- school_dta %>%
  mutate(share_desk=1-(m4scq11_inpt)/(m4scq4_inpt))


#Used ICT 
school_teacher_questionnaire_INPT <- teachers_dta %>%
  group_by(school_code) %>%
  summarise(used_ict_pct=mean(m3sbq4_inpt, na.rm=TRUE))

school_dta <- school_dta %>%
  mutate(used_ict_num=case_when(
    m1sbq12_inpt==0  ~ 0,
    (m1sbq12_inpt>=1 ) ~ m1sbq13a_inpt_etri,
    (is.na(m1sbq12_inpt==0) | is.na(m1sbq13a_inpt_etri)) ~ as.numeric(NA)
  ))

#access to ICT
school_dta <- school_dta %>%
  mutate(access_ict=case_when(
    m1sbq12_inpt==0 | m1sbq13_inpt==0 ~ 0,
    (m1sbq12_inpt>=1 & m1sbq13_inpt==1 ) ~ 1,
    (m1sbq12_inpt>=1 & m1sbq13_inpt==1 ) ~ 0.5, #Internet didn't work when tested
    (is.na(m1sbq12_inpt==0) | is.na(m1sbq13_inpt) ) ~ as.numeric(NA)
  ))



inpt_list<-c('blackboard_functional', 'share_textbook', 'share_pencil','share_exbook', 'pens_etc', 'textbooks', 'share_desk',  'used_ict', 'access_ict')

school_dta <- school_dta %>%
  left_join(school_teacher_questionnaire_INPT) %>%
  mutate(used_ict=if_else((used_ict_pct>=0.5 & used_ict_num>=3), 1,0))     %>%  #Set percentage of teachers to use ICT over 50% and number over 3
  mutate(inputs=textbooks+blackboard_functional + pens_etc + share_desk +  0.5*used_ict + 0.5*access_ict) 


ggpairs(school_dta, columns=c("blackboard_functional", "share_textbook", "share_pencil", "share_exbook",   "share_desk", "used_ict", "access_ict" ), title="Inputs and Infrastructure") +
  theme_bw()


#validate 
out <- confront(school_dta, INPT_rules)
summary(out)
plot(out)


```
## School Infrastructure

```{r infra}


#############################################
##### School Infrastructure ###########
#############################################

# School survey. Total score starts at 1 and points added are the sum of whether a school has: 
#   - Access to adequate drinking water 
# -Functional toilets.  Extra points available if are separate for boys/girls, private, useable, and have hand washing facilities 
# - Electricity  in the classroom 
# - Internet
# - School is accessible for those with disabilities (road access, a school ramp for wheelchairs, an entrance wide enough for wheelchairs, ramps to classrooms where needed, accessible toilets, and disability screening for seeing, hearing, and learning disabilities with partial credit for having 1 or 2 or the 3).)

#drinking water
school_dta <- school_dta %>%
  #
  mutate(drinking_water=if_else((m1sbq9_infr==1 | m1sbq9_infr==2 | m1sbq9_infr==5 | m1sbq9_infr==6), 1,0, as.numeric(NA) ))

#functioning toilets
school_dta <- school_dta %>%
  mutate(toilet_exists=if_else(m1sbq1_infr==7 ,0,1),
         toilet_separate=if_else((m1sbq2_infr==1 | m1sbq2_infr==3),1,0),
         toilet_private=as.numeric(m1sbq4_infr),
         toilet_usable=as.numeric(m1sbq5_infr),
         toilet_handwashing=as.numeric(m1sbq7_infr),
         toilet_soap=as.numeric(m1sbq8_infr)) %>%
  mutate(functioning_toilet=case_when(
    # exist, separate for boys/girls, clean, private, useable,  handwashing available
    toilet_exists==1 & toilet_usable==1 & toilet_separate==1  & toilet_private==1  & toilet_handwashing==1 ~ 1,
    toilet_exists==0 | toilet_usable==0 | toilet_separate==0  | toilet_private==0  | toilet_handwashing==0 ~ 0
  )) 

#visibility
school_dta <- school_dta %>%
  mutate(visibility=case_when(
    m4scq10_inpt==1 &  m4scq8_inpt==1  ~ 1,
    m4scq10_inpt==0 & m4scq8_inpt==1 ~ 0)) 

#electricity
school_dta <- school_dta %>%
  mutate(class_electricity=if_else(m1sbq11_infr==1,1,0)) 


#accessibility for people with disabilities
school_dta <- school_dta %>%
  mutate(
    disab_road_access=bin_var(m1s0q2_infr,1),
    disab_school_ramp=case_when(
      m1s0q3_infr==0 ~ 1,
      (m1s0q4_infr	==1 & m1s0q3_infr	==1) ~ 1,
      (m1s0q4_infr	==0 & m1s0q3_infr	==1) ~ 0,
      is.na(m4scq1_infr) ~ as.numeric(NA)),
    disab_school_entr=bin_var(m1s0q5_infr,1),
    disab_class_ramp=case_when(
      m4scq1_infr==0 ~ 1,
      (m4scq1_infr==1 & m4scq1_infr==1) ~ 1,
      (m4scq1_infr==0 & m4scq1_infr==1) ~ 0,
      is.na(m4scq1_infr) ~ as.numeric(NA)),
    disab_class_entr=bin_var(m4scq3_infr,1),
    disab_screening=rowMeans(select(.,m1sbq17_infr__1,m1sbq17_infr__2,m1sbq17_infr__3), na.rm = TRUE),
    #sum up all components for overall disability accessibility score
    disability_accessibility=(disab_road_access+disab_school_ramp+disab_school_entr+
                                disab_class_ramp+disab_class_entr+
                                if_else(m1sbq1_infr==7,0,as.numeric(m1sbq6_infr))+
                                disab_screening)/7
  ) %>%
  mutate(internet=case_when(
    m1sbq15_inpt==2  ~ 1,
    m1sbq15_inpt==1  ~ 0.5,
    m1sbq15_inpt==0   ~ 0,
    is.na(as.numeric(m1sbq15_inpt)) ~ 0,
    TRUE ~ 0) ) # 1 point if internet working, 0.5 if doesn't work well, 0 if not at all


infr_list<-c('drinking_water', 'functioning_toilet', 'internet',  'class_electricity', 'disability_accessibility')

school_dta <- school_dta %>%
  mutate(n_mssing_INFR=n_miss_row(.)) %>%
  mutate(infrastructure=(drinking_water+ functioning_toilet+ internet + class_electricity+ disability_accessibility))


ggpairs(school_dta, columns=c("drinking_water", "functioning_toilet", "internet",    "class_electricity", "disability_accessibility" ), title="Inputs and Infrastructure") +
  theme_bw()


#validate 
out <- confront(school_dta, INFR_rules)
summary(out)
plot(out)
```

# School Management

## Operational Management

```{r OPMN}

#############################################
##### School Operational Management ###########
#############################################

#Princials/head teachers are given two vignettes:
#- One on solving the problem of a hypothetical leaky roof 
#- One on solving a problem of inadequate numbers of textbooks.  
#Each vignette is worth 2 points.  
#
#The indicator will measure two things: presence of functions and quality of functions. In each vignette: 
#- 0.5 points are awarded for someone specific having the responsibility to fix 
#- 0.5 point is awarded if the school can fully fund the repair, 0.25 points is awarded if the school must get partial help from the community, and 0 points are awarded if the full cost must be born by the community 
#- 1 point is awarded if the problem is fully resolved in a timely manner, with partial credit given if problem can only be partly resolved.

school_dta <- school_dta %>%
  mutate(
    vignette_1_resp=if_else((m7sbq1_opmn==0 & (m7sbq4_opmn==4 | m7sbq4_opmn==98)), 0, 0.5),
    vignette_1_finance=case_when(
      m7sbq2_opmn==1 ~ 0.5,
      (m7sbq2_opmn==2 | m7sbq2_opmn==97) ~ 0.25,
      m7sbq2_opmn==3 ~ 0,
      m7sbq1_opmn==0 & !(m7sbq4_opmn==4 | m7sbq4_opmn==98) ~ 0.5),
    vignette_1_address=if_else(m7sbq1_opmn==1, case_when(
      m7sbq3_opmn==1 ~ 0,
      (m7sbq3_opmn==2 | m7sbq3_opmn==97) ~ .5,
      m7sbq3_opmn==3 ~ 1),
      case_when(
        m7sbq5_opmn==1 ~ 0,
        m7sbq5_opmn==2 ~ .5,
        m7sbq5_opmn==3 ~ 1))) %>% 
  #give total score for this vignette
  mutate(vignette_1=vignette_1_resp+vignette_1_finance+vignette_1_address) %>% 
  mutate(vignette_2_resp=if_else(m7scq1_opmn==98, 0, 0.5), # no one responsible that is known
         vignette_2_finance=if_else(m7scq1_opmn==1,0,0.5),      #parents are forced to buy textbooks          
         #give partial credit based on how quickly it will be solved <1 month, 1-3, 3-6, 6-12, >1 yr
         vignette_2_address=case_when(
           m7scq2_opmn==1 ~ 1,
           m7scq2_opmn==2 ~ .75,
           m7scq2_opmn==3 ~ .5,
           m7scq2_opmn==4 ~ .25,
           (m7scq2_opmn==5 |m7scq2_opmn==98) ~ 0)) %>%
  mutate(vignette_2=vignette_2_resp+vignette_2_finance+vignette_2_address) %>%          #sum all components for overall score
  mutate(operational_management=1+vignette_1+vignette_2 )


ggpairs(school_dta, columns=c("vignette_1", "vignette_2", "operational_management" ), title="Operational Management") +
  theme_bw()


#validate 
out <- confront(school_dta, OPMN_rules)
summary(out)
plot(out)

```

## Instructional Leadership

```{r}


#############################################
##### School Instructional Leadership ###########
#############################################

# School survey. Total score starts at 1 and points added are the sum of whether a teacher has: 
# - Had a classroom observation in past year 
# - Had a discussion based on that observation that lasted longer than 10 min 
# - Received actionable feedback from that observation 
# - Teacher had a lesson plan and discussed it with another person

#list additional info that will be useful to keep in each indicator dataframe
preamble_info_teacher_drop_ildr <- c('interview__key', 'questionnaire_roster_id', 'teacher_name', 'teacher_number', 
                                     'available', 'teacher_position', 'teacher_grd1', 'teacher_grd2', 'teacher_grd3', 'teacher_grd4', 
                                     'teacher_language', 'teacher_math', 'teacher_both_subj', 'teacher_other_subj', 'teacher_education', 'teacher_year_began',
                                     'teacher_age')

teachers_dta <- teachers_dta %>%
  mutate(classroom_observed=bin_var(m3sdq15_ildr,1),
         classroom_observed_recent=if_else((classroom_observed==1 & m3sdq16_ildr<=12),1,0), #set recent to mean under 12 months
         purpose_observation=case_when(
           m3sdq18_ildr__1==1 ~ "Evaluation",
           m3sdq18_ildr__2==1 ~ "Professional Development",
           m3sdq18_ildr__3==1 ~ "Monitoring",
           m3sdq18_ildr__97==1 ~ m3sdq18_other_ildr ),
         discussion_30_min=bin_var(m3sdq20_ildr,3),
         discussed_observation=if_else((classroom_observed==1 & m3sdq19_ildr==1 & m3sdq20_ildr>=2),1,0), #make sure there was discussion and lasted more than 10 min
         feedback_observation=if_else((m3sdq21_ildr==1 & (m3sdq22_ildr__1==1 | m3sdq22_ildr__2==1 | m3sdq22_ildr__3==1
                                                          | m3sdq22_ildr__4==1 | m3sdq22_ildr__5==1)),1,0), #got feedback and was specific
         lesson_plan=if_else(m3sdq23_ildr==1,1,0),
         lesson_plan_w_feedback=if_else((m3sdq23_ildr==1 & m3sdq24_ildr==1),1,0)) %>%
  mutate(feedback_observation=if_else(m3sdq15_ildr==1 & m3sdq19_ildr==1, feedback_observation, 0)) %>% #fix an issue where teachers that never had classroom observed arent asked this question.
  mutate(instructional_leadership=1+0.5*classroom_observed + 0.5*classroom_observed_recent + discussed_observation + feedback_observation + lesson_plan_w_feedback) %>%
  mutate(instructional_leadership=if_else(classroom_observed==1,instructional_leadership, 1.5 + lesson_plan_w_feedback )) 

ggpairs(teachers_dta, columns=c("classroom_observed", "classroom_observed_recent", "discussed_observation",
                                             "feedback_observation", "lesson_plan_w_feedback","instructional_leadership"), title="Instructional Leadership ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, ILDR_rules)
summary(out)
plot(out)

```

## Principal School Knowledge

```{r PKNW}



#############################################
##### School Principal School Knowledge ###########
#############################################
# The aim of this indicator is to measure the extent to which principals have the knowledge about their own schools that is necessary for them to be effective managers. A score from 1 to 5 capturing the extent to which the principal is familiar with certain key aspects of the day-to-day workings of the school (in schools that have principals). Principal receives points in the following way: 
#   - 5 points. Principal gets all 90-100% of questions within accuracy bounds (defined below). 
# - 4 points. Principal gets 80-90% of question within accuracy bounds. 
# - 3 points. Principal gets 70-80% of question within accuracy bounds. 
# - 2 points. Principal gets 60-70% of question within accuracy bounds. 
# - 1 points. Principal gets under 60% of question within accuracy bounds. 
# 
# Accuracy bounds for each question. 
# Within 1 teacher/student for each of the following: 
#   - Out of these XX teachers, how many do you think would be able to correctly add triple digit numbers (i.e. 343+215+127)? 
#   - Out of these XX teachers, how many do you think would be able to correctly to multiply double digit numbers (i.e. 37 x 13)? 
#   - Out of these XX teachers, how many do you think would be able to complete sentences with the correct world (i.e. The accident ___ (see, saw, had seen, was seen) by three people)? 
#   - Any of these XX teachers have less than 3 years of experience? 
#   - Out of these XX teachers, which ones have less than 3 years of experience as a teacher? 
# Within 3 teacher/student for each of the following: 
#   - In the selected 4th grade classroom, how many of the pupils have the relevant textbooks? 
#   Must identify whether or not blackboard was working in a selected 4th grade classroom.




#first create a database containing actual values for each question for the principal
pknw_actual_cont <- teachers_dta %>%
  select(school_code, m5_teach_count, m5s2q1c_number, m5s2q1e_number, m5s1q1f_grammer ) %>%
  group_by(school_code) %>%
  summarise_all( ~(if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))

pknw_actual_exper <- teachers_dta %>%
  select(school_code, m3sb_tnumber, m3sb_troster,m3saq5, m3saq6 ) %>%
  mutate(experience=(as.numeric(year)-m3saq5)) %>%
  filter(experience <3) %>% 
  group_by(school_code) %>%
  summarise(teacher_count_experience_less3=n())


school_dta <- school_dta %>%
  left_join(pknw_actual_cont) %>%
  left_join(pknw_actual_exper) %>%
  mutate(teacher_count_experience_less3=if_else(is.na(teacher_count_experience_less3), as.numeric(0), as.numeric(teacher_count_experience_less3)),
         m5s2q1c_number=m5s2q1c_number*m5_teach_count,
         m5s2q1e_number=m5s2q1e_number*m5_teach_count,
         m5s1q1f_grammer=m5s1q1f_grammer*m5_teach_count)


#create function to compare principal responses to actual
# if principal is within 1 student/teacher, then score as 1, 0 otherwise
principal_scorer <- function(var_guess, var_actual, var_total, margin1, margin2) {
  if_else(
    ((1-abs(var_guess-var_actual)/var_total>= as.numeric(margin1)) | (var_guess-var_actual <= as.numeric(margin2))),
    1,
    0)
}



school_dta <- school_dta %>%
  mutate_at(vars(starts_with('m7sfq5_pknw'), starts_with('m7sfq6_pknw'), starts_with('m7sfq7_pknw')), ~if_else(is.na(.),as.numeric(NA),1)) %>%
  mutate(add_triple_digit_pknw=principal_scorer(rowSums(select(.,starts_with('m7sfq5_pknw')), na.rm=T), m5s2q1c_number, m7_teach_count_pknw,0.8,1),
         multiply_double_digit_pknw=principal_scorer(rowSums(select(.,starts_with('m7sfq6_pknw')), na.rm=T), m5s2q1e_number, m7_teach_count_pknw,0.8,1),
         complete_sentence_pknw=principal_scorer(rowSums(select(.,starts_with('m7sfq7_pknw')), na.rm=T), m5s1q1f_grammer, m7_teach_count_pknw,0.8,1),
         experience_pknw=principal_scorer(m7sfq9_pknw_filter, teacher_count_experience_less3, m7_teach_count_pknw,0.8,1),
         textbooks_pknw=principal_scorer(m7sfq10_pknw, m4scq5_inpt, m4scq4_inpt,0.8,3),
         blackboard_pknw=if_else(m7sfq11_pknw==blackboard_functional,1,0)) %>%
  mutate(principal_knowledge_avg=rowMeans(select(.,add_triple_digit_pknw, multiply_double_digit_pknw, complete_sentence_pknw, experience_pknw, textbooks_pknw, blackboard_pknw), na.rm=TRUE)) %>%
  mutate(principal_knowledge_score=case_when(
    principal_knowledge_avg ==1 ~ 5,
    (principal_knowledge_avg >=5/6 & principal_knowledge_avg<1) ~ 4,
    (principal_knowledge_avg >=4/6 & principal_knowledge_avg<5/6) ~ 3,
    (principal_knowledge_avg >=3/6 & principal_knowledge_avg<4/6) ~ 2,
    (principal_knowledge_avg <3/6 ) ~ 1  )
  ) 




ggpairs(school_dta, columns=c("add_triple_digit_pknw", "multiply_double_digit_pknw", "complete_sentence_pknw",
                                             "experience_pknw", "textbooks_pknw","blackboard_pknw",
                                             "principal_knowledge_score"), title="Principal Knowledge ") +
  theme_bw()


#validate 
out <- confront(school_dta, PKNW_rules)
summary(out)
plot(out)

```
## Principal Management Skills

```{r}
#############################################
##### School Principal Management Skills ###########
#############################################


# Score of 1-5 based on sum of following: 
#   - 1 Point. School Goals Exists 
# - 1 Point. School goals are clear to school director, teachers, students, parents, and other members of community (partial credit available) 
# - 1 Point. Specific goals related to improving student achievement ( improving test scores, improving pass rates, reducing drop out, reducing absenteeism, improving pedagogy, more resources for infrastructure, more resources for inputs) 
# - 1 Point. School has defined system to measure goals (partial credit available)

#Create variables for whether school goals exists, are clear, are relevant to learning, and are measured in an appropriate way.


school_dta <- school_dta %>%
  mutate(sch_goals_exist=bin_var(m7sdq1_pman,1),
         sch_goals_clear=if_else(m7sdq1_pman==1, 
                                    rowMeans(select(.,m7sdq3_pman__1, m7sdq3_pman__2, m7sdq3_pman__3, m7sdq3_pman__4, m7sdq3_pman__5), na.rm=TRUE),
                                    0) ,
         sch_goals_relevant_total=rowSums(select(.,m7sdq4_pman__1, m7sdq4_pman__2, m7sdq4_pman__3, m7sdq4_pman__4, m7sdq4_pman__5, m7sdq4_pman__6, m7sdq4_pman__7, m7sdq4_pman__8, m7sdq4_pman__97), na.rm=TRUE),
         sch_goals_relevant=if_else(m7sdq1_pman==1, 
                                       case_when(
                                         (sch_goals_relevant_total > 0) ~ 1,
                                         (sch_goals_relevant_total == 0) ~ 0),
                                       0),
         sch_goals_measured=if_else((m7sdq1_pman==1), 
                                       case_when(
                                         (m7sdq5_pman==1) ~ 0,
                                         (m7sdq5_pman==2 | m7sdq5_pman==97 ) ~ 0.5,
                                         (m7sdq5_pman==3) ~ 1),
                                       0)) %>%
  mutate(goal_setting=1+sch_goals_exist+sch_goals_clear+sch_goals_relevant+sch_goals_measured) %>%
  # Now for problem solving
  mutate(
    problem_solving_proactive=case_when(
      (m7seq1_pman==4 ) ~ 1,
      (m7seq1_pman==2 | m7seq1_pman==3 ) ~ 0.5,
      (m7seq1_pman==1 | m7seq1_pman==98 ) ~ 0,
      TRUE ~ 0),
    problem_solving_info_collect=(m7seq2_pman__1+m7seq2_pman__2 + m7seq2_pman__3 + m7seq2_pman__4)/4,
    problem_solving_stomach=case_when(
      (m7seq3_pman==4 ) ~ 1,
      (m7seq3_pman==3 ) ~ 0.5,
      (m7seq3_pman==1 | m7seq3_pman==2 | m7seq3_pman==98 ) ~ 0.25,
      TRUE ~ 0)
    
  ) %>%
  mutate(problem_solving=1+(4/3)*problem_solving_proactive+(4/3)*problem_solving_info_collect+(4/3)*problem_solving_stomach) %>%
  
  
  mutate(principal_management=(goal_setting+problem_solving)/2)



ggpairs(school_dta, columns=c("problem_solving",
                                             "goal_setting",
                                             "principal_management"), title="Principal Management ") +
  theme_bw()


#validate 
out <- confront(school_dta, PMAN_rules)
summary(out)
plot(out)

```

# Teacher Policies

## Teacher Teaching Attraction

```{r TATT}
#############################################
##### Teacher Teaching Attraction ###########
#############################################

# In the school survey, a number of De Facto questions on teacher attraction are asked. 0.8 points is awarded for each of the following: 
#   - 0.8 Points. Teacher satisfied with job 
# - 0.8 Points. Teacher satisfied with status in community 
# - 0.8 Points. Would better teachers be promoted faster? 
#   - 0.8 Points. Do teachers receive bonuses? 
#   - 0.8 Points. One minus the fraction of months in past year with a salary delay.


#create function to clean teacher attitudes questions.  Need to reverse the order for scoring for some questions.  
#Should have thought about this, when programming in Survey Solutions and scale 1-5.

attitude_fun  <- function(x) {
  case_when(
    x==99 ~ as.numeric(NA),
    x==4 ~ 5,
    x==3 ~ 3.67,
    x==2 ~ 2.33,
    x==1 ~ 1
  )
}

attitude_fun_rev  <- function(x) {
  case_when(
    x==99 ~ as.numeric(NA),
    x==1 ~ 5,
    x==2 ~ 3.67,
    x==3 ~ 2.33,
    x==4 ~ 1
  )
}


teachers_dta <- teachers_dta %>%
  mutate(teacher_satisfied_job=attitude_fun_rev(m3seq1_tatt)/5,
         teacher_satisfied_status=attitude_fun_rev(m3seq2_tatt)/5,
         better_teachers_promoted=bin_var(m3seq3_tatt,1),
         teacher_bonus=bin_var(m3seq4_tatt,1),
         teacher_bonus_attend=if_else(m3seq4_tatt==1,
                                      bin_var(m3seq5_tatt__1,1),
                                      0),
         teacher_bonus_student_perform=if_else(m3seq4_tatt==1,
                                               bin_var(m3seq5_tatt__2,1),
                                               0),
         teacher_bonus_extra_duty=if_else(m3seq4_tatt==1,
                                          bin_var(m3seq5_tatt__3,1),
                                          0),
         teacher_bonus_hard_staff=if_else(m3seq4_tatt==1,
                                          bin_var(m3seq5_tatt__4,1),
                                          0),
         teacher_bonus_subj_shortages=if_else(m3seq4_tatt==1,
                                              bin_var(m3seq5_tatt__5,1),
                                              0),
         teacher_bonus_add_qualif=if_else(m3seq4_tatt==1,
                                          bin_var(m3seq5_tatt__6,1),
                                          0),
         teacher_bonus_school_perform=if_else(m3seq4_tatt==1,
                                              bin_var(m3seq5_tatt__7,1),
                                              0),
         teacher_bonus_other=if_else(m3seq4_tatt==1,
                                     if_else(m3seq5_tatt__97==1,m3seq5_other_tatt,"NA"),
                                     "NA"),
         salary_delays=if_else(m3seq6_tatt==1, m3seq7_tatt,0)) %>%
  mutate(salary_delays=if_else(salary_delays>12,12,salary_delays)) %>%
  mutate(teacher_attraction=1+0.8*teacher_satisfied_job+.8*teacher_satisfied_status+.8*better_teachers_promoted+.8*teacher_bonus+.8*(1-salary_delays/12))




ggpairs(teachers_dta, columns=c("teacher_satisfied_job",
                                             "teacher_satisfied_status",
                                             "better_teachers_promoted",
                                             "teacher_bonus",
                                             "salary_delays",
                                             "teacher_attraction"), title="Principal Management ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TATT_rules)
summary(out)
plot(out)

```

##  Teaching Selection and Deployment

```{r TSDP}


#############################################
##### Teacher Teaching Selection and Deployment ###########
#############################################

# School Survey. The De Facto portion of the Teacher Selection and Deployment Indicator considers two issues: how teachers are selected into the profession and how teachers are assigned to positions (transferred) once in the profession. Research shows that degrees and years of experience explanin little variation in teacher quality, so more points are assigned for systems that also base hiring on content knowledge or pedagogical skill. 2 points are available for the way teachers are selected and 2 points are available for deployment. 
# 
# Selection 
# - 0 Points. None of the below 
# - 1 point. Teachers selected based on completion of coursework, educational qualifications, graduating from tertiary program (including specialized programs), selected based on experience 
# - 2 points. Teacher recruited based on passing written content knowledge test, passed interview stage assessment, passed an assessment conducted by supervisor based on practical experience, conduct during mockup class. 
# 
# Deployment 
# - 0 Points. None of the below 
# - 1 point. Teachers deployed based on years of experience or job title hierarchy 
# - 2 points. Teacher deployed based on performance assessed by school authority, colleagues, or external evaluator, results of interview.


teachers_dta <- teachers_dta %>%
  mutate(
    teacher_selection=case_when(
      (m3sdq1_tsdp__5==1 | m3sdq1_tsdp__6==1 | m3sdq1_tsdp__8==1 | m3sdq1_tsdp__9==1 )  ~ 2,
      (m3sdq1_tsdp__1==1 | m3sdq1_tsdp__2==1 | m3sdq1_tsdp__3==1 | m3sdq1_tsdp__4==1 | m3sdq1_tsdp__7==1) ~ 1,
      (m3sdq1_tsdp__1==0 & m3sdq1_tsdp__2==0 & m3sdq1_tsdp__3==0 & m3sdq1_tsdp__4==0 & m3sdq1_tsdp__5==0 & m3sdq1_tsdp__6==0 & m3sdq1_tsdp__7==0 & m3sdq1_tsdp__8==0 & m3sdq1_tsdp__9==0) ~ 0
    ),
    teacher_deployment=case_when(
      (m3seq8_tsdp__3==1 | m3seq8_tsdp__4==1 | m3seq8_tsdp__5==1  )  ~ 2,
      (m3seq8_tsdp__1==1 | m3seq8_tsdp__2==1 | m3seq8_tsdp__97==1) ~ 1,
      ((m3seq8_tsdp__1==0 & m3seq8_tsdp__2==0 & m3seq8_tsdp__3==0 & m3seq8_tsdp__4==0 & m3seq8_tsdp__5==0) | ( m3seq8_tsdp__99==1)) ~ 0
      
    )
  ) %>%
  mutate(teacher_selection_deployment=1+teacher_selection+teacher_deployment)



ggpairs(teachers_dta, columns=c(
                                             "teacher_selection",
                                             "teacher_deployment",
                                             "teacher_selection_deployment"), title="Teacher Selection and Deployment ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TSDP_rules)
summary(out)
plot(out)

```


```{r tsup}


#############################################
##### Teacher Teaching Support ###########
#############################################


# School survey. Our teaching support indicator asks teachers about participation and the experience with several types of formal/informal training: 
#   
#   Pre-Service (Induction) Training: 
#   - 0.5 Points. Had a pre-service training 
# - 0.5 Points. Teacher reported receiving usable skills from training 
# 
# Teacher practicum (teach a class with supervision) 
# - 0.5 Points. Teacher participated in a practicum 
# - 0.5 Points. Practicum lasted more than 3 months and teacher spent more than one hour per day teaching to students. 
# 
# In-Service Training: 
#   - 0.5 Points. Had an in-service training 
# - 0.25 Points. In-service training lasted more than 2 total days 
# - 0.125 Points. More than 25% of the in-service training was done in the classroom. 
# - 0.125 Points. More than 50% of the in-service training was done in the classroom. 
# 
# Opportunities for teachers to come together to share ways of improving teaching: 
#   - 1 Point if such opportunities exist.



teachers_dta <- teachers_dta %>%
  mutate(opportunities_teachers_share=bin_var(m3sdq14_ildr,1)) %>%
  mutate(pre_training_exists=bin_var(m3sdq3_tsup,1)/2,
         pre_training_useful=if_else(m3sdq3_tsup==1,
                                     bin_var(m3sdq4_tsup,1),
                                     0)/2,
         pre_training_practicum=bin_var(m3sdq6_tsup,1)/2,
         pre_training_practicum_lngth=case_when(
           (m3sdq6_tsup==1 & m3sdq7_tsup>=3 & m3sdq8_tsup>=1) ~  0.5,
           (m3sdq6_tsup==1 & (m3sdq7_tsup<3 | m3sdq8_tsup<1))  ~ 0,
           m3sdq6_tsup==2 ~ 0,
           TRUE ~ 0),
         in_service_exists=bin_var(m3sdq9_tsup,1),
         in_servce_lngth=case_when(
           (m3sdq9_tsup==1 & m3sdq10_tsup>2 ) ~ 1,
           (m3sdq9_tsup==1 & m3sdq10_tsup<=2) ~ 0,
           m3sdq9_tsup==0 ~ 0,
           TRUE ~ 0
         ),
         in_service_classroom=case_when(
           (m3sdq9_tsup==1 & m3sdq13_tsup>=3)  ~ 1,
           (m3sdq9_tsup==1 & m3sdq13_tsup==2)  ~ 0.5,
           (m3sdq9_tsup==1 & m3sdq13_tsup==1)  ~ 0,
           m3sdq9_tsup==0 ~ 0,
           TRUE ~ 0
         )
  ) %>%
  mutate(pre_service=pre_training_exists+pre_training_useful,
         practicum=pre_training_practicum+pre_training_practicum_lngth,
         in_service=0.5*in_service_exists+0.25*in_servce_lngth+0.25*in_service_classroom) %>%
  mutate(teacher_support=1+pre_service+practicum+in_service+opportunities_teachers_share) 
# mutate(teacher_support=if_else(teacher_support>5,5,teacher_support)) #need to fix






ggpairs(teachers_dta, columns=c(
                                             "pre_service", "pre_training_exists", "pre_training_useful",
                                             "practicum", "pre_training_practicum", "pre_training_practicum_lngth",
                                             "in_service", "in_service_exists", "in_servce_lngth", "in_service_classroom",
                                             "teacher_support"), title="Teacher Support ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TSUP_rules)
summary(out)
plot(out)
```

## Teacher Evaluation

```{r tevl}

#############################################
##### Teacher Teaching Evaluation ###########
#############################################

# School survey. This policy lever measures whether there is a teacher evaluation system in place, and if so, the types of decisions that are made based on the evaluation results. Score is the sum of the following: 
#   - 1 Point. Was teacher formally evaluated in past school year? 
#   - 1 Point total. 0.2 points for each of the following: Evaluation included evaluation of attendance, knowledge of subject matter, pedagogical skills in the classroom, students' academic achievement, students' socio-emotional development 
# - 1 Point. Consequences exist if teacher receives 2 or more negative evaluations 
# - 1 Point. Rewards exist if teacher receives 2 or more positive evaluations


#list of teacher evluation questions
tevl<-c(
  'm3sbq7_tmna__1', 'm3sbq7_tmna__2', 'm3sbq7_tmna__3', 'm3sbq7_tmna__4','m3sbq7_tmna__5', 'm3sbq7_tmna__6', 'm3sbq7_tmna__97',
  'm3sbq8_tmna__2', 'm3sbq8_tmna__3', 'm3sbq8_tmna__4','m3sbq8_tmna__5', 'm3sbq8_tmna__6', 'm3sbq8_tmna__7', 'm3sbq8_tmna__8', 'm3sbq8_tmna__97', 'm3sbq8_tmna__98',
  'm3sbq9_tmna__1', 'm3sbq9_tmna__2', 'm3sbq9_tmna__3', 'm3sbq9_tmna__4', 'm3sbq9_tmna__7', 'm3sbq9_tmna__97', 'm3sbq9_tmna__98',
  'm3bq10_tmna__1', 'm3bq10_tmna__2', 'm3bq10_tmna__3', 'm3bq10_tmna__4', 'm3bq10_tmna__7', 'm3bq10_tmna__97', 'm3bq10_tmna__98')



teachers_dta<- teachers_dta %>%
  mutate(formally_evaluated=bin_var(m3sbq6_tmna,1),
         evaluation_content=if_else(m3sbq6_tmna==1,
                                    (m3sbq8_tmna__1+m3sbq8_tmna__2+ m3sbq8_tmna__3 + m3sbq8_tmna__5 + m3sbq8_tmna__6)/5,
                                    0),
         negative_consequences=case_when(
           (m3sbq9_tmna__1==1 | m3sbq9_tmna__2==1 | m3sbq9_tmna__3==1 | m3sbq9_tmna__4==1 | m3sbq9_tmna__97==1) ~ 1,
           (is.na(m3sbq9_tmna__1) & is.na(m3sbq9_tmna__2) & is.na(m3sbq9_tmna__3) & is.na(m3sbq9_tmna__4) & is.na(m3sbq9_tmna__97)) ~ as.numeric(NA),
           TRUE ~ 0),
         positive_consequences=case_when(
           (m3bq10_tmna__1==1 | m3bq10_tmna__2==1 | m3bq10_tmna__3==1 | m3bq10_tmna__4==1 | m3bq10_tmna__97==1) ~ 1,
           (is.na(m3bq10_tmna__1) & is.na(m3bq10_tmna__2) & is.na(m3bq10_tmna__3) & is.na(m3bq10_tmna__4) & is.na(m3bq10_tmna__97)) ~ as.numeric(NA),
           TRUE ~ 0)
  ) %>%
  mutate(teaching_evaluation=1+formally_evaluated+evaluation_content+negative_consequences+positive_consequences)



ggpairs(teachers_dta, columns=c(
                                             "formally_evaluated", "evaluation_content", "negative_consequences",
                                             "positive_consequences", 
                                             "teaching_evaluation"), title="Teacher Evaluation ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TEVL_rules)
summary(out)
plot(out)

```


```{r tmna}



#############################################
##### Teacher  Monitoring and Accountability ###########
#############################################

# School Survey. This policy lever measures the extent to which teacher presence is being monitored, whether attendance is rewarded, and whether there are consequences for chronic absence. Score is the sum of the following: 
#   - 1 Point. Teachers evaluated by some authority on basis of absence. 
# - 1 Point. Good attendance is rewarded. 
# - 1 Point. There are consequences for chronic absence (more than 30% absence). 
# - 1 Point. One minus the fraction of teachers that had to miss class because of any of the following: collect paycheck, school administrative procedure, errands or request of the school district office, other administrative tasks.




teachers_dta <- teachers_dta %>%
  mutate(attendance_evaluated=if_else(m3sbq6_tmna==1,
                                      case_when(
                                        (m3sbq8_tmna__1==1) ~ 1,
                                        TRUE ~ 0
                                      ),
                                      0),
         attendance_rewarded=if_else(m3seq4_tatt==1,
                                     case_when(
                                       (m3seq5_tatt__1==1) ~ 1,
                                       TRUE ~ 0
                                     ),
                                     0),
         attendence_sanctions=case_when(
           (m3sbq2_tmna__1==1 | m3sbq2_tmna__2==1 | m3sbq2_tmna__3==1 | m3sbq2_tmna__4==1 | m3sbq2_tmna__97==1) ~ 1,
           (is.na(m3sbq2_tmna__1) & is.na(m3sbq2_tmna__2) & is.na(m3sbq2_tmna__3) & is.na(m3sbq2_tmna__4) & is.na(m3sbq2_tmna__97)) ~ as.numeric(NA),
           TRUE ~ 0
         ),
         miss_class_admin=case_when(
           (m3sbq1_tatt__1==1 | m3sbq1_tatt__2==1 | m3sbq1_tatt__3==1 | m3sbq1_tatt__97==1) ~ 1,
           (m3sbq1_tatt__1==0 & m3sbq1_tatt__2==0 & m3sbq1_tatt__3==0 & m3sbq1_tatt__97==0) ~ 0,
           
           TRUE ~ as.numeric(NA)
         )
  )  %>%
  mutate(teacher_monitoring=1+attendance_evaluated + 1*attendance_rewarded + 1*attendence_sanctions + (1-miss_class_admin))


ggpairs(teachers_dta, columns=c(
                                             "attendance_evaluated", "attendance_rewarded", "attendence_sanctions",
                                             "miss_class_admin", 
                                             "teacher_monitoring"), title="Teacher Monitoring & Accountability ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TMNA_rules)
summary(out)
plot(out)
```
## Intrinsic Motivation

```{r}

#############################################
##### Teacher  Intrinsic Motivation ###########
#############################################

# 
# School Survey. This lever measures whether teachers are intrinsically motivated to teach. The question(s) aim to address this 
# phenomenon by measuring the level of intrinsic motivation among teachers as well as teacher values that may be relevant for 
# ensuring that the teacher is motivated to focus on all children and not just some. Average score (1 (worst) - 5 (best)) on items 
# given to teachers on intrinsic motivation.

intrinsic_motiv_q_rev <- c('m3scq1_tinm','m3scq2_tinm', 'm3scq3_tinm', 'm3scq4_tinm', 'm3scq5_tinm', 'm3scq6_tinm',
                           'm3scq7_tinm', 'm3scq10_tinm')

intrinsic_motiv_q <- c( 'm3scq11_tinm', 'm3scq14_tinm')

intrinsic_motiv_q_all <- c('m3scq1_tinm','m3scq2_tinm', 'm3scq3_tinm', 'm3scq4_tinm', 'm3scq5_tinm', 'm3scq6_tinm',
                           'm3scq7_tinm', 'm3scq10_tinm', 'm3scq11_tinm', 'm3scq14_tinm')



teachers_dta <- teachers_dta %>%
  mutate(    
    SE_PRM_TINM_1 = 100*if_else(m3scq1_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if the ~
    SE_PRM_TINM_2 = 100*if_else(m3scq2_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if stud~
    SE_PRM_TINM_3 = 100*if_else(m3scq3_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with It is acceptable for a teacher to be absent if the ~
    SE_PRM_TINM_4 = 100*if_else(m3scq4_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they attend scho~
    SE_PRM_TINM_5 = 100*if_else(m3scq5_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they come to sch~
    SE_PRM_TINM_6 = 100*if_else(m3scq6_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students deserve more attention if they are motivat~
    SE_PRM_TINM_7 = 100*if_else(m3scq7_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students have a certain amount of intelligence and ~
    SE_PRM_TINM_8 = 100*if_else(m3scq10_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with To be honest, students can't really change how inte~
    SE_PRM_TINM_9 = 100*if_else(m3scq11_tinm>=3,1,0),  #(De Facto) Percent of teachers that agree or strongly agrees with Students can always substantially change how intell~
    SE_PRM_TINM_10 = 100*if_else(m3scq14_tinm>=3,1,0) #(De Facto) Percent of teachers that agree or strongly agrees with /"Students can change even their basic intelligence l~
  ) %>%
  mutate_at(intrinsic_motiv_q_rev, attitude_fun_rev ) %>%
  mutate_at(intrinsic_motiv_q, attitude_fun ) %>%
  mutate(acceptable_absent=(m3scq1_tinm+ m3scq2_tinm + m3scq3_tinm)/3,
         students_deserve_attention=(m3scq4_tinm+ m3scq5_tinm + m3scq6_tinm )/3,
         growth_mindset=(m3scq7_tinm + m3scq10_tinm + m3scq11_tinm + m3scq14_tinm)/4,
         motivation_teaching=case_when(
           is.na(m3scq15_tinm__3) ~ as.numeric(NA),
           m3scq15_tinm__3>=1 ~ 0,
           (m3scq15_tinm__3<1 & (m3scq15_tinm__1>=1 | m3scq15_tinm__2>=1 | m3scq15_tinm__4>=1 | m3scq15_tinm__5>=1)) ~ 1,
           TRUE ~ as.numeric(NA)
         )) %>%
  mutate(intrinsic_motivation=1+0.8*(0.2*acceptable_absent + 0.2*students_deserve_attention + 0.2*growth_mindset + motivation_teaching+bin_var(m3sdq2_tmna,1))) 



ggpairs(teachers_dta, columns=c(
                                             "acceptable_absent", "students_deserve_attention", "growth_mindset",
                                             "motivation_teaching", "m3sdq2_tmna",
                                             "intrinsic_motivation"), title="Teacher Intrinsic Motivation ") +
  theme_bw()


#validate 
out <- confront(teachers_dta, TINM_rules)
summary(out)
plot(out)
```
# Input and Infrastructure Policies

```{r}
#############################################
##### School  Inputs and Infrastructure Standards ###########
#############################################
#   - 1 Point. Are there standards in place to monitor blackboard and chalk, pens and pencils, basic classroom furniture, computers, textbooks, exercise books, toilets, electricity, drinking water, accessibility for those with disabilities? (partial credit available) 

school_dta <- school_dta %>%
  mutate(standards_monitoring_input=rowMeans(.[grep(x=colnames(school_dta), 
                                                    pattern="m1scq13_imon_")], na.rm=TRUE),
         standards_monitoring_infra=rowMeans(.[grep(x=colnames(school_dta), 
                                                             pattern="m1scq14_imon_")], na.rm=TRUE) ) %>%
  mutate(standards_monitoring=1+(standards_monitoring_input*6+standards_monitoring_infra*4)*0.4)

ggpairs(school_dta, columns=c(
                                             "standards_monitoring_infra", 
                                             "standards_monitoring_input",
                                             "standards_monitoring"), title="Standards ") +
  theme_bw()


#validate 
out <- confront(school_dta, ISTD_rules)
summary(out)
plot(out)
```

```{r}
#############################################
##### School  Inputs and Infrastructure Monitoring ###########
#############################################

# School Survey. A score of 1-5 based on 3 factors. Each factor has received an equal weight in terms of points. The factors are the following: 
#-	Someone is monitoring 
#-	System for monitoring available (E.g. inventory)
#-	Community involved in monitoring 


school_dta <- school_dta %>%
  mutate(m1scq3_imon=bin_var(m1scq3_imon,1),
         system_in_place=case_when(
           m1scq5_imon==0 ~ 0,
           m1scq5_imon==1 ~ 1,
           m1scq5_imon==2 ~ 0.5,
           TRUE ~ 0
         )) %>%
  mutate(monitoring_inputs=if_else(m1scq1_imon==1,
                                   rowMeans(.[grep(x=colnames(school_dta), 
                                                   pattern="m1scq4_imon_")], na.rm=TRUE),
                                   0),
         monitoring_infrastructure=if_else(m1scq7_imon==1,
                                           rowMeans(.[grep(x=colnames(school_dta), 
                                                           pattern="m1scq9_imon_")], na.rm=TRUE),
                                           0),
  ) %>%
  mutate(parents_involved=if_else(m1scq3_imon==1,1,0,0)) %>%
  mutate(sch_monitoring=1+(monitoring_inputs+monitoring_infrastructure)/2+system_in_place+parents_involved)



ggpairs(school_dta, columns=c(
                                             "monitoring_inputs", 
                                             "monitoring_infrastructure",
                                             "system_in_place",
                                             "parents_involved",
                                             "sch_monitoring"), title="Monitoring ") +
  theme_bw()


#validate 
out <- confront(school_dta, IMON_rules)
summary(out)
plot(out)
```

# School Management Policies


##  School Management - Clarity of Functions

```{r}
#############################################
  ##### School School Management Clarity of Functions  ###########
  #############################################
  
  school_dta <- school_dta %>%
    mutate(infrastructure_scfn=if_else((m7sfq15a_pknw__0==1 | m7sfq15a_pknw__98==1),0,1),
           materials_scfn=if_else((m7sfq15b_pknw__0==1 | m7sfq15b_pknw__98==1),0,1),
           hiring_scfn=if_else((m7sfq15c_pknw__0==1 | m7sfq15c_pknw__98==1),0,1),
           supervision_scfn=if_else((m7sfq15d_pknw__0==1 | m7sfq15d_pknw__98==1),0,1),
           student_scfn=if_else((m7sfq15e_pknw__0==1 | m7sfq15e_pknw__98==1),0,1),
           principal_hiring_scfn=if_else((m7sfq15f_pknw__0==1 | m7sfq15f_pknw__98==1),0,1),
           principal_supervision_scfn=if_else((m7sfq15g_pknw__0==1 | m7sfq15g_pknw__98==1),0,1)
    ) %>%
    mutate(sch_management_clarity=1+
             (infrastructure_scfn+materials_scfn)/2+
             (hiring_scfn + supervision_scfn)/2 +
             student_scfn +
             (principal_hiring_scfn+ principal_supervision_scfn)/2
    )

  
ggpairs(school_dta, columns=c(
                                             "infrastructure_scfn", 
                                             "materials_scfn",
                                             "hiring_scfn",
                                             "supervision_scfn",
                                             "student_scfn",
                                             "principal_hiring_scfn",
                                             "sch_management_clarity"
                                             ), title="Clarity of Functions ") +
  theme_bw()


#validate 
out <- confront(school_dta, SCFN_rules)
summary(out)
plot(out)

```


##  School Management - Attraction

```{r}

#############################################
  ##### School School Management Attraction  ###########
  #############################################
  
  # This policy lever measures whether the right candidates are being attracted to the profession of school principals. The questions will aim to capture the provision of benefits to attract and maintain the best people to serve as principals. 
  # 
  # Scoring: 
  #   -score is between 1-5 based on how satisfied the principal is with status in community. We will also add in component based on Principal salaries.
  # For salary, based GDP per capita from 2020 World Bank  https://data.worldbank.org/indicator/NY.GDP.PCAP.PP.CD?locations=NE.  
  
  #get gdp per capita, PPP info

call_yr <- as.numeric(year)-2
  gdp_sal <- wbstats::wb_data(
    country=country,
    indicator='NY.GDP.PCAP.CN',
    mrv=1
  ) 

  sal_denom=gdp_sal$NY.GDP.PCAP.CN[1]
  
  
  school_dta <- school_dta %>%
    mutate(principal_satisfaction=attitude_fun_rev(m7shq1_satt),
           m7shq2_satt=if_else(m7shq2_satt<0,as.numeric(NA),m7shq2_satt),
           #m7shq2_satt=if_else(m7shq2_satt<100,m7shq2_satt*10000,m7shq2_satt),
           principal_salary=if_else(m7shq2_satt==999, as.numeric(NA),12*m7shq2_satt/sal_denom	)) %>%
    mutate(
      principal_salary_score=case_when(
        between(principal_salary,0,0.5) ~ 1,
        between(principal_salary,0.5,0.75) ~ 2,
        between(principal_salary,0.75,1) ~ 3,
        between(principal_salary,1,1.5) ~ 4,
        principal_salary>=1.5 ~ 5,
        principal_salary<0 ~ as.numeric(NA))) %>%
    mutate(sch_management_attraction=(principal_satisfaction+principal_salary_score)/2)
  
  

ggpairs(school_dta, columns=c(
                                             "principal_satisfaction", 
                                             "principal_salary_score",
                                             "sch_management_attraction"
                                             ), title="Attraction") +
  theme_bw()


#validate 
out <- confront(school_dta, SATT_rules)
summary(out)
plot(out)
```

##  School Management - Selection and Deployment 

```{r}
  
  #############################################
  ##### School School Management Selection and Deployment  ###########
  #############################################
  
  
  # This policy lever measures whether the right candidates being selected. These questions will probe what the recruitment process is like to 
  # ensure that these individuals are getting the positions. The question would ultimately be based on: 1) there is a standard approach for selecting principals,
  # 2) that approach relies on professional/academic requirements, and 3) those requirements are common in practice. 
  # 
  # Scoring: 
  #   - 1 (lowest score) Most important factor is political affiliations or ethnic group. 
  # - 2 Political affiliations or ethnic group is a consideration, but other factors considered as well. 
  # - 3 Most important factor is years of experience, good relationship with owner/education department, and does not factor in quality teaching, demonstrated management qualities, or knowledge of local community. 
  # - 4 Quality teaching, demonstrated management qualities, or knowledge of local community is a consideration in hiring, but not the most important factor 
  # - 5 Quality teaching, demonstrated management qualities, or knowledge of local community is the most important factor in hiring.
  

school_dta <- school_dta %>%
  mutate(sch_selection_deployment=case_when(
    (m7sgq2_ssld==2 | m7sgq2_ssld==3 | m7sgq2_ssld==8) ~ 5,
    (m7sgq2_ssld==6 | m7sgq2_ssld==7) ~ 1,
    (!(m7sgq2_ssld==6 | m7sgq2_ssld==7) & (m7sgq1_ssld__2==1 | m7sgq1_ssld__3==1 | m7sgq1_ssld__8==1) ) ~ 4,
    (!(m7sgq2_ssld==6 | m7sgq2_ssld==7) & (m7sgq1_ssld__1==1 | m7sgq1_ssld__4==1 | m7sgq1_ssld__5==1 | m7sgq1_ssld__97==1) ) ~ 3,
    (m7sgq1_ssld__6==1 | m7sgq1_ssld__7==1 ) ~ 2, 
    TRUE ~ as.numeric(NA))
  )


  
ggpairs(school_dta, columns=c(
                                             "m7sgq2_ssld", 
                                             "sch_selection_deployment"
                                             ), title="Attraction") +
  theme_bw()


#validate 
out <- confront(school_dta, SSLD_rules)
summary(out)  
plot(out)
```


##  School Management - Support

```{r}

  #############################################
  ##### School School Management Support  ###########
  #############################################
  
  
  # This policy lever measures the extent to which principals receive training and/or exposure to other professional opportunities that could help them be better school leaders. 
  # The questions aim to figure out if such programs are provided, and if they are, their level of quality. 
  # 
  # Scoring (sum of components below): 
  #   - 1 Point. Principal has received formal training on managing school. 
  # - 1/3 Point. Had management training for new principals. 
  # - 1/3 Point. Had management in-service training. 
  # - 1/3 Point. Had mentoring/coaching by experienced principals. 
  # - 1 Point. Have used skills gained at training. 
  # - 1 Point. Principals offered training at least once per year
  
  school_dta <- school_dta %>%
    mutate(prinicipal_trained=bin_var(m7sgq3_ssup,1),
           principal_training=if_else(m7sgq3_ssup==1,
                                      rowMeans(.[grep(x=colnames(school_dta), 
                                                      pattern="m7sgq4_ssup_")], na.rm=TRUE),
                                      0),
           principal_used_skills=if_else(m7sgq3_ssup==1,
                                         bin_var(m7sgq5_ssup,1),0),
           principal_offered=if_else((m7sgq7_ssup==2 | m7sgq7_ssup==3 | m7sgq7_ssup==4 | m7sgq7_ssup==5),1,0)
    ) %>%
    mutate(sch_support=1+prinicipal_trained+principal_training+principal_used_skills+principal_offered)
  

  
ggpairs(school_dta, columns=c(
                                             "prinicipal_trained", 
                                             "principal_training",
                                             "principal_used_skills",
                                             "principal_offered",
                                             "sch_support"
                                             ), title="Support") +
  theme_bw()


#validate 
out <- confront(school_dta, SSUP_rules)
summary(out)
plot(out)
```

##  School Management - Evaluation

```{r}
 #############################################
  ##### School School Management Evaluation  ###########
  #############################################
  
  # School Survey. This policy lever measures the extent to which principal performance is being monitored and enforced via accountability measures. 
  # The idea is that the indicator will be based on: 1) there is a legislation outlining the need to monitor, 2) principals are being evaluated, 3) 
  # principals are being evaluated on multiple things, and 4) there the accountability mechanisms in place.
  
  
  
  school_dta<- school_dta %>%
    mutate(principal_formally_evaluated=bin_var(m7sgq8_sevl,1),
           principal_eval_tot=rowSums(.[grep(x=colnames(school_dta), 
                                             pattern="m7sgq10_sevl_")], na.rm=TRUE)-m7sgq10_sevl__98) %>%
    mutate(principal_evaluation_multiple=if_else(m7sgq8_sevl==1,
                                                 case_when(
                                                   principal_eval_tot>=5 ~ 1,
                                                   (principal_eval_tot>1 & principal_eval_tot<5) ~ 0.666667,
                                                   principal_eval_tot==1 ~ 0.3333333,
                                                   TRUE ~ 0
                                                 ),
                                                 0),
           principal_negative_consequences=case_when(
             (m7sgq11_sevl__1==1 | m7sgq11_sevl__2==1 | m7sgq11_sevl__3==1 | m7sgq11_sevl__4==1 | m7sgq11_sevl__97==1) ~ 1,
             TRUE ~ 0),
           principal_positive_consequences=case_when(
             (m7sgq12_sevl__1==1 | m7sgq12_sevl__2==1 | m7sgq12_sevl__3==1 | m7sgq12_sevl__4==1 | m7sgq12_sevl__97==1) ~ 1,
             TRUE ~ 0)
    ) %>%
    mutate(principal_evaluation=1+principal_formally_evaluated+principal_evaluation_multiple+principal_negative_consequences+principal_positive_consequences)
  
  
ggpairs(school_dta, columns=c(
                                             "principal_formally_evaluated", 
                                             "principal_evaluation_multiple",
                                             "principal_negative_consequences",
                                             "principal_positive_consequences",
                                             "principal_evaluation"
                                             ), title="Evaluation") +
  theme_bw()


#validate 
out <- confront(school_dta, SEVL_rules)
summary(out)  
plot(out)
```


# Save

```{r}

################################
#Store Key Created Datasets
################################

save(school_dta, teachers_dta, fourth_grade, first_grade,
     file = here(processed_dir,"School","Confidential","Cleaned", "cleaned_R.Rdata"))

#save individually as dta files
write_dta(school_dta, here(processed_dir,"School","Confidential","Cleaned", "school_R.dta"))
write_dta(teachers_dta, here(processed_dir,"School","Confidential","Cleaned", "teachers_R.dta"))
write_dta(fourth_grade, here(processed_dir,"School","Confidential","Cleaned", "fourth_grade_R.dta"))
write_dta(first_grade, here(processed_dir,"School","Confidential","Cleaned", "first_grade_R.dta"))



```

